---
title: "ER interpolation (avg/campaign)"
author: "Benoît D'ANGELO"
date: "21 avril 2016"
output:
  html_document:
    code_folding: hide
    fig_height: 3
    fig_width: 7
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../mod_toc.html"> Calibration </a></h3>
***

# Introduction

## Objectives

Calculate the ER fluxes interpolation across the measurement year

## Output

One file is generated:

* prediction_ER.csv (contains ER interpolated fluxes for different models)

# Setup

## Load packages and set paths

```{r ld_pckg, message=FALSE}
# File name : /2013_spavar_LG/report/modelisation/calibration/ER_perCampaign_int.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade packages (see "Howto" page to install them)
library(bdphdtoolbox)     # personnal toolbox

# CRAN packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)
library(rprojroot)  # allow easier relative path

# Find project root
r <- rprojroot::is_rstudio_project
root <- r$find_file()

# Folder to save graphes
savpth <- file.path(root, "graphs", "carbonbalance", "ecosyst", "interpolation")

# allow wider tables and graphes in html output
options(width = 100)
knitr::opts_chunk$set(comment=NA,warning = FALSE)

# Load custom color set
source(file.path(root, "src", "report", "custom_colors.R"))
source(file.path(root, "src", "report", "custom_themes.R"))
```

```{r ld_plot_custom_fn}
# X axis setup
x <- seq(as.Date("2013-03-01"), as.Date("2015-03-31"), by="2 months")
labels <- date_format("%b")(x)
breaks <- seq(as.POSIXct("2013-03-01"), as.POSIXct("2015-03-31"), by="2 months")

# plot function
plt_interp <- function(df){
  p <- ggplot(dfp, aes(x=date, y=ER))+
  geom_line(data = dat, aes(x=timestamp, y=pER), color=gris)+
  geom_point(color=drouge, size=3)+
  ylim(0,22)+
  geom_linerange(data = dfp, aes(x=date, ymin=ER-ER_sd, ymax=ER+ER_sd), color=drouge)+
  labs(y=expression(paste("RE modélisée (", mu, mol,m^-2,s^-1,")", sep="")), x="2013-2014")+
  scale_x_datetime(breaks=breaks, labels = labels,limits=range(breaks))+
  theme_interp
  return(p)
}
```

## Load data

```{r ld_data_continuous}
# Load CONTINOUS DATA treated data (generated with gather_interpol_data.R)
dfc <- read.csv(file.path(root, "data","processed", "env_var_interp.csv"))%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))
```

```{r ld_data_ponctual}
# Load PONCTUAL DATA treated data (generated with getClean_fluxesFC)
# Campaign average
dfp <- read.csv(file.path(root, "data","processed", "cl_fluxesFC_avg.csv"))%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))
```

```{r load_mdl_par}
# Load models parameters
ERpar <- read.csv(file.path(root, "data","processed", "ER_mdlpar.csv"))
```

# Calculations
```{r mdl_calc}
mdl_ls <- c("exp-Tair", "exp-T5", "exp-Tair_H", "exp-Tair_IVcov", "exp-T5_H", "exp-T5_IVcov")

prediction <- data.frame()
for (j in mdl_ls){
    dat <- prd_seldat(df=dfc, id_eq = j) # Select data
    par <- prd_gpar(id_eq = j, dfparam = ERpar) # Select parameter
    var <- prd_prpdat(dat) # response variable only
    pER <- gpER(df=var, p=par) # prep data and calc pred
    tpER <- data.frame(mdl=j, timestamp=dfc$timestamp, pER=pER)
    prediction <- rbind(prediction,tpER)
}

prediction$timestamp <- as.POSIXct(prediction$timestamp, format="%Y-%m-%d %H:%M:%S")
```

```{r, cumulated_flux}
# Convertion fact from umol.m2.s1 to gC.m2.hour
cfA_hr <- (3600)*1e-6*12

output <- prediction %>%
  mutate(yr = ifelse(timestamp <= as.POSIXct("2014-02-19 12:00:00", format="%Y-%m-%d %H:%M:%S"), "2013", "2014"))%>%
  group_by(mdl, yr)%>%
  mutate(pER_gC = pER*cfA_hr) %>% # conversion en gC.m2.h
  summarise(pER_gC = sum(pER_gC, na.rm=T))%>%
  mutate(pER_gC = pER_gC*365/362) # Correction car années de 362 jours

output_yr <- output %>%
  filter(yr %in% c(2013, 2014))%>%
  select(mdl, pER_gC, yr)%>%
  spread(yr, pER_gC)%>%
  mutate(all =(`2013`+`2014`)/2)
as.data.frame(output_yr)
```

# Graphs {.tabset}

## ER~aexp(bTair)

```{r}
# Select model
dat <- filter(prediction, mdl == "exp-Tair")#%>%
# Plot interpolation
rm(p)
p <- plt_interp(dat)+
  annotate("text", x=as.POSIXct("2015-01-01"), y=18, label="RE-1", size=5)
p
# Save plot
ggsave("ER_BdCitp_Ta.pdf", plot=p, path=savpth, width=7, height=3, cairo_pdf)
```

## ER~(aIV+c)exp(bTair)

```{r}
# Select model
dat <- filter(prediction, mdl == "exp-Tair_IVcov")#%>%
# Plot interpolation
rm(p)
p <- plt_interp(dat)+
  annotate("text", x=as.POSIXct("2015-01-01"), y=18, label="RE-2", size=5)
p
# Save plot
ggsave("ER_BdCitp_TaIVcov.pdf", plot=p, path=savpth, width=7, height=3, cairo_pdf)
```

## ER~(aH+c)exp(bTair)

```{r}
# Select model
dat <- filter(prediction, mdl == "exp-Tair_H")#%>%
# Plot interpolation
p <- plt_interp(dat)+
  annotate("text", x=as.POSIXct("2015-01-01"), y=18, label="RE-3", size=5)
p
# Save plot
ggsave("ER_BdCitp_TaH.pdf", plot=p, path=savpth, width=7, height=3, cairo_pdf)
```

## ER~aexp(bT5)

```{r}
# Select model
dat <- filter(prediction, mdl == "exp-T5")#%>%
# Plot interpolation
p <- plt_interp(dat)#+
  # annotate("text", x=as.POSIXct("2015-01-01"), y=18, label="RE-1", size=5)
p
# Save plot
ggsave("ER_BdCitp_T5.pdf", plot=p, path=savpth, width=7, height=3, cairo_pdf)
```

## ER~(aIV+c)exp(bT5)

```{r}
# Select model
dat <- filter(prediction, mdl == "exp-T5_IVcov")#%>%
# Plot interpolation
p <- plt_interp(dat)#+
  # annotate("text", x=as.POSIXct("2015-01-01"), y=18, label="RE-2", size=5)
p
# Save plot
ggsave("ER_BdCitp_T5IVcov.pdf", plot=p, path=savpth, width=7, height=3, cairo_pdf)
```

## ER~(aH+c)exp(bT5)

```{r}
# Select model
dat <- filter(prediction, mdl == "exp-T5_H")#%>%
# Plot interpolation
rm(p)
p <- plt_interp(dat)#+
  # annotate("text", x=as.POSIXct("2015-01-01"), y=18, label="RE-3", size=5)
p
# Save plot
ggsave("ER_BdCitp_T5H.pdf", plot=p, path=savpth, width=7, height=3, cairo_pdf)
```
