---
title: "Ecosystem Respiration (ER)"
author: "Benoît D'ANGELO"
date: "23/02/2015"
output:
  html_document:
    code_folding: hide
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../vis_toc.html"> Visualisation </a></h3>
  
***

# Setup

## Load packages and functions

```{r setup, message=FALSE, warning=FALSE}
# File name : /2013_spavar_LG/report/visualisation/flux/ER.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade package
library(laguettevarspa) # "spatial variability" data
library(bdphdtoolbox)
# See "Howto"" page to install it

# CRAN package
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# Figure save path
savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/visualisation"

# Home made functions
source("../../../src/report/vis_plot.R")
# source("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/src/report/vis_plot.R")
# functions: flplt, p7_fl_plt, ann_month_mean_fl, month_mean_fl

# Load custom color set
source("../../../src/report/custom_colors.R")
# source("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/src/report/custom_colors.R")
```

## Load and transform data

```{r load_data, echo=TRUE}
# Load data from package (laguettevarspa)
df <- svNetFlux %>%
  filter(type == "ER")%>%
  separate(date, c("year","month", "day"),remove = F) %>%
  separate(timestamp, c("ts_date", "time"), sep=" ") %>%
  mutate(time = substr(time, 1, 5), ID_camp = as.factor(ID_camp))

# Average data by campaign
mdf <- df %>%
  group_by(ID_camp)%>%
  summarise(netCO2F_sd=sd(netCO2F),netCO2F=mean(netCO2F), date=mean(date))%>%
  separate(date, c("year","month", "day"),remove = F)

# Average data by measurement point
mpdf <- df %>%
  group_by(placette)%>%
  filter(ID_camp == 6)%>%
  summarise(netCO2F_sd=sd(netCO2F),netCO2F=mean(netCO2F))%>%
  arrange(netCO2F)

# Setup Y axis label
lab_Y <- expression(paste("Re (", mu, mol,m^-2,s^-1,")", sep=""))
```

# Annual ER variation 

## Annual ER average

```{r, comment=NULL}
aa <- df %>%
  group_by(year) %>%
  summarise(ER = round(mean(netCO2F, na.rm=T),2), ER_sd = round(sd(netCO2F, na.rm=T),2))

as.data.frame(aa)
```


## All data points {.tabset}


### All data

```{r}
# Observation number
nobs <- paste("N :", as.character(NROW(df)))
# quality criteria on R2
df$colR2 <- ifelse(df$R2 >= 0.8, ">= 0.8", "< 0.8")
```

```{r raw data, message=FALSE, fig.width=9}
flplt(df, lab_Y)+ # plot function location: /src/report/vis_plot
  geom_point(aes(color=colR2), shape=21, size=4)+
  theme(legend.position=c(.9,.9), legend.key=element_blank())
ggsave("ER_evolution.pdf", path=savpth)
```

### Averaged by campaign (B&W)

```{r, fig.width=9}
ggplot(mdf, aes(x=date, y=netCO2F))+
  geom_point(size=3)+
  annotate("text", x=as.Date("2015-03-01"), y=12, label="B", size=5)+
  geom_linerange(aes(x=date, ymin=netCO2F-netCO2F_sd, ymax=netCO2F+netCO2F_sd))+
  labs(y=lab_Y, x="")+
  scale_x_date(breaks = date_breaks("2 months"), labels = date_format("%b"))+
  theme_classic()+
  theme(plot.margin=unit(c(0,0,0,0),"mm"))
ggsave("ER_evolution_avg.pdf", path=savpth, width=7, height=3)
```

### Averaged by campaign (color)

```{r, fig.width=9}
### DIAPO
ggplot(mdf, aes(x=date, y=netCO2F))+
  geom_point(size=3, color=drouge)+
  annotate("text", x=as.Date("2015-02-01"), y=15, label="N=20", size=4)+
  #2013
  annotate("text", x=as.Date("2013-06-15"), y=15, label="2013", size=5)+
  annotate("text", x=as.Date("2013-12-01"), y=5.27, label="4,27", size=5, color=orange)+
  annotate("segment", x=as.Date("2013-03-05"), xend=as.Date("2013-12-15"), y=4.27, yend=4.27, linetype="dashed", size=1, color=orange)+
  #2014
  annotate("text", x=as.Date("2014-06-15"), y=15, label="2014", size=5)+
  annotate("text", x=as.Date("2014-12-01"), y=4.63, label="3,63", size=5, color=orange)+
  annotate("segment", x=as.Date("2014-03-15"), xend=as.Date("2014-12-15"), y=3.63, yend=3.63, linetype="dashed", size=1, color=orange)+
  geom_linerange(aes(x=date, ymin=netCO2F-netCO2F_sd, ymax=netCO2F+netCO2F_sd), color=drouge)+
  labs(y=lab_Y, x="")+
  scale_x_date(breaks = date_breaks("2 months"), labels = date_format("%b"))+
  theme_classic()+
  theme(plot.margin=unit(c(0,0,0,0),"mm"))
ggsave("VS_RE_avg.pdf", path=savpth, width=7, height=3)
```

### Averaged by campaign (data)

```{r, results="asis"}
tbl <- as.data.frame(mdf[,1:4])%>%
  mutate(ER=round(netCO2F, 2), ER_sd=round(netCO2F_sd,2))%>%
  select(ID_camp, date, ER, ER_sd)

knitr::kable(tbl, caption="ER fluxes averaged by campaign")
```

## Individual measurement points

```{r, fig.width=10, fig.height=6}
p7_fl_plt(df, lab_Y)+ # plot function location: /src/report/vis_plot
  geom_point(aes(color=colR2))+
  scale_colour_manual(values=c("red","black"))
ggsave("ER_p7_evolution.pdf", path=savpth)
```
  
# Autre

## Annual mean differences significance:

```{r}
A <- filter(df, year==2013)
B <- filter(df, year==2014)
t.test(A$netCO2F, B$netCO2F)
```

## Normality test:

The normality tests are available [here](flux_norm_test.html)

## Montly ER means per year

```{r, echo=TRUE}
ann_month_mean_fl(df, lab_Y) # plot function location: /src/report/vis_plot
```

## Montly ER mean (pooling all years)

```{r, echo=TRUE}
month_mean_fl(df, lab_Y) # plot function location: /src/report/vis_plot
```
