---
title: "Méthane"
author: "Benoît D'ANGELO"
date: "21/07/2015"
output:
  html_document:
    code_folding: hide
    fig_height: 3
    fig_width: 7
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../vis_toc.html"> Visualisation </a></h3>
***

# Setup

## Load packages and set paths

```{r, message=FALSE}
# File name : /2013_spavar_LG/report/visualisation/flux/methane.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade packages (see "Howto" page to install them)
library(laguettevarspa) # spatial variability data
library(snoweather)     # weather station data
library(bdphdtoolbox)

# CRAN packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)

# Folder to save graphes
savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/visualisation"

# Folder to save data treatement
outpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed"

# allow wider tables and graphes in html output
options(width = 100)

# Load custom color set
source("../../../src/report/custom_colors.R")
# source("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/src/report/custom_colors.R")
```

## Load and transform data

```{r}
# Load data from package (laguettevarspa)
all <- svCH4 %>%
  separate(date, c("year","month", "day"),remove = F)%>%
  mutate(date=as.Date(date, format="%Y-%m-%d"))%>%
  filter(CH4 < 1, plot != "ETREPEE")

# Average data by campaign and measurement point
m <- all %>%
  group_by(date, plot)%>%
  summarise(CH4=mean(CH4, na.rm=T))

# Average data by campaign
mm <- all %>%
  group_by(ID_camp)%>%
  summarise(date=min(date, na.rm=T), CH4_sd=sd(CH4, na.rm=T), CH4=mean(CH4, na.rm=T), N=n())
```

# Annual CH4 variation 

## Annual CH4 average

```{r, comment=NULL}
aa <- all %>%
  group_by(year) %>%
  summarise(CH4_m = round(mean(CH4, na.rm=T),2), CH4_sd = round(sd(CH4, na.rm=T),2))

as.data.frame(aa)
```

## All data points {.tabset}

All CH4 measurements point on La Guette peatland, excluding CARBIODIV measurements but including the other "non-spatial variability" measurement point (ETREPEE and 5bis plot for instance)

### All data 

```{r, raw data , message=FALSE, fig.width=9}
ggplot(all , aes(x=date, y=CH4, color=plot))+
  geom_point(size=3)+
  theme_bw()
```

### mean per plot

```{r, fig.width=9}
ggplot(m, aes(x=date, y=CH4, color=plot))+
  geom_point(size=3)+
  theme_bw()
```

### Averaged by campaign (B&W)

```{r, fig.width=9}
ggplot(mm, aes(x=date, y=CH4))+
  geom_point(size=3)+
  geom_linerange(aes(x=date, ymin=CH4-CH4_sd, ymax=CH4+CH4_sd))+
  # xlim(as.Date("2013-04-23"), as.Date("2015-02-01"))+
  labs(y=expression(paste("CH"[4], " (", mu, mol,m^-2,s^-1,")", sep="")), x="2013-2014")+
  scale_x_date(breaks = date_breaks("2 months"), labels = date_format("%b"))+
  theme_classic()+
  theme(plot.margin=unit(c(0,0,0,0),"mm"))
ggsave("CH4_evolution_avg.pdf", path=savpth, width=7, height=3)
```

TODO : same with VS data only

### Averaged by campaign (color)

```{r, fig.width=9}
ggplot(mm, aes(x=date, y=CH4))+
  geom_point(size=3, color=drouge)+
  annotate("text", x=as.Date("2015-01-01"), y=0.30, label="N=5", size=4)+
  #2013
  annotate("text", x=as.Date("2013-06-15"), y=0.30, label="2013", size=5)+
  annotate("text", x=as.Date("2013-12-05"), y=0.05, label="0,04", size=5, color=orange)+
  annotate("segment", x=as.Date("2013-03-05"), xend=as.Date("2013-12-15"), y=0.04, yend=0.04, linetype="dashed", size=1, color=orange)+
  #2014
  annotate("text", x=as.Date("2014-06-15"), y=0.30, label="2014", size=5)+
  annotate("text", x=as.Date("2014-12-11"), y=0.11, label="0,10", size=5, color=orange)+
  annotate("segment", x=as.Date("2014-03-15"), xend=as.Date("2014-12-15"), y=0.10, yend=0.10, linetype="dashed", size=1, color=orange)+
  geom_linerange(aes(x=date, ymin=CH4-CH4_sd, ymax=CH4+CH4_sd), color=drouge)+
  labs(y=expression(paste("CH"[4], " (", mu, mol,m^-2,s^-1,")", sep="")), x="")+
  scale_x_date(breaks = date_breaks("2 months"), labels = date_format("%b"))+
  theme_classic()+
  theme(plot.margin=unit(c(0,0,0,0),"mm"))
ggsave("VS_CH4_avg.pdf", path=savpth, width=7, height=3)
```

