---
title: "Calibration ch4 (moy/campagne)"
author: "Benoît D'ANGELO"
date: "14 avril 2016"
output:
  html_document:
    code_folding: hide
    fig_height: 3
    fig_width: 7
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../mod_toc.html"> Modélisation </a></h3>
***

# Objectives
This files describe the calibration of the CH4 fluxes. 2 files are generated:

* CH4_mdl_par.csv (contains models parameters)
* CH4_pred_cal.csv (contains models parameters)

# Setup

## Load packages and set paths

```{r ld_pckg, message=FALSE}
# File name : /2013_spavar_LG/report/modelisation/calibration/ch4_perCampaign_cal.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade packages (see "Howto" page to install them)
library(bdphdtoolbox)     # personnal toolbox

# CRAN packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)
library(rprojroot)
## Find project root
r <- rprojroot::is_rstudio_project
root <- r$find_file()
## Folder to save the treatements
outpath <- file.path(root, "data", "processed")

# allow wider tables and graphes in html output
options(width = 100)

# Load custom color set
source(file.path(root, "src", "report", "custom_colors.R"))
```

## Load functions

```{r ld_fn}
# model calculations for exponential equation
calc_mdl_exp <- function(df, nb_var){ # identique ER... sauf start
    if(nb_var == 1){
      m <- nls(Y ~ a * exp(b*X1), data=df, start=list(a=0.1, b=0.01), na.action = na.exclude)
    }else if (nb_var == 2){
      m <- nls(Y ~ (a*X2 + c) * exp(b*X1), data=df, start=list(a=0.3, b=0.1, c=1), na.action = na.exclude)
    }else if (nb_var == 3){
      m <- nls(Y ~ (a*X2 + c*X3) * exp(b*X1), data=df, start=list(a=0.3, b=0.1, c=1), na.action = na.exclude)
    }else if (nb_var > 3){
      cat("variable number > 3, not implemented yet")
    }else{
      cat("error: (no variable ?)")
    }
    return(m)
}

# model calculations for linear equation
calc_mdl_lin <- function(df, nb_var){
    if(nb_var == 1){
    m <- nls(Y ~ a + b*X1, data=df, start=list(a=0.1, b=0.01), na.action = na.exclude)
    }else if (nb_var == 2){
      cat("not done yet")
    }else if (nb_var > 2){
      cat("variable number > 2, not implemented yet")
    }else{
      cat("error: (no variable ?)")
    }
    return(m)
}

# models calculation redirection depending on the equation type (lin, exp...)
calc_mdl <- function(df, id_eq){
  # id the model
  eq_type <- prd_idfy(id_eq)[1]
  nb_var <- as.numeric(prd_idfy(id_eq)[2])
  vars <- prd_idfy(id_eq)[-c(1,2)]
  # find equation, calculate mdl
  if(eq_type == "exp"){
    m <- calc_mdl_exp(df, nb_var)
  }else if(eq_type == "lin"){
    m <- calc_mdl_lin(df, nb_var)
  }else if(eq_type == "pwr"){
    m <- calc_mdl_pwr(df, nb_var)
  }else{
    cat("Unknown equation type")
  }
}

mdl_param <- function(df, mdl){
  # R2
  devmean <- df$Y-(mean(df$Y)) # deviation à la moyenne
  SSres <-sum((resid(mdl))^2) # Total sum of squares
  SStot <- sum(devmean^2) # Residual sum of squares
  # 2 way to calculate
  # R2 <- (SStot-SSres)/SStot 
  R2 <- 1 - SSres/SStot
  # Adjusted R2
  N <- NROW(devmean) # sample size
  p <- 1 # number of predictors
  R2a <- 1-((1-R2)*(N-1))/(N-p-1)
  # RMSE
  rmse_mdl <- sqrt(mean(((predict(mdl))-df$Y)^2,na.rm=TRUE))
  nrmse_mdl <- 100*rmse_mdl/mean(df$Y)
  # Collect usefull param
  df <- data.frame(a=coef(mdl)[1],
                   b=coef(mdl)[2],
                   c=coef(mdl)[3],
                   a_se=coef(summary(mdl))[,"Std. Error"][1],
                   b_se=coef(summary(mdl))[,"Std. Error"][2],
                   c_se=coef(summary(mdl))[,"Std. Error"][3],
                   a_pval=coef(summary(mdl))[,"Pr(>|t|)"][1],
                   b_pval=coef(summary(mdl))[,"Pr(>|t|)"][2],
                   c_pval=coef(summary(mdl))[,"Pr(>|t|)"][3],
                   R2=R2,
                   aR2=R2a,
                   rmse=rmse_mdl,
                   nrmse=nrmse_mdl,
                   aic=AIC(mdl),
                   bic=BIC(mdl))
  return(df)
}
```

## Load and transform data

```{r ld_data}
# Load treated data (generated with getClean_fluxesFC)
df <- read.csv(file.path(root, "data", "processed", "cl_fluxesFC.csv"))%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))

# Load treated data (generated with getClean_fluxesFC)
dfm <- read.csv(file.path(root, "data", "processed", "cl_fluxesFC_avg.csv"))%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))
```

# Calculations
```{r mdl_calc}
mdlpar <- data.frame()

mdl_ls <- c("lin-IVcov", "exp-IVcov", "lin-H", "exp-H", "lin-A","exp-A", "exp-Tair", "exp-T40", "exp-T80")

for(i in mdl_ls){
  # data selection
  dft <- na.omit(prd_seldat(df=dfm, flux="CH4", id_eq = i))
  colnames(dft) <- prd_prpdat(dft, T)
  # equation selection
  mdl <- calc_mdl(dft, id_eq=i)
  par <- mdl_param(dft, mdl)
  par$mdl <- i # add id_eq to df
  mdlpar <- rbind(mdlpar, par)
}
```

```{r mdl_output}
result <- mdlpar %>%
  select(mdl, a, b, c, a_pval, b_pval, c_pval, R2, aR2, rmse, nrmse, aic, bic)%>%
  mutate_each(funs(round(.,2)), a, b, c, a_pval, b_pval, c_pval, R2, aR2, rmse, nrmse, aic, bic)
```

## Models

```{r}
result
```

## Models sort by R2a

```{r}
mdlpar %>%
  select(mdl, R2, aR2, rmse, nrmse, aic, bic)%>%
  arrange(desc(aR2))%>%
  mutate_each(funs(round(.,2)), R2, aR2, rmse, nrmse, aic, bic)

mdlpar %>%
  select(mdl, a, b, c, a_se, b_se, c_se, a_pval, b_pval, c_pval)%>%
  mutate_each(funs(round(.,2)), a, b, c, a_se, b_se, c_se, a_pval, b_pval, c_pval)

mdlparls <- mdlpar %>%
  select(mdl, a, b, c)
```

```{r}
prediction <- data.frame()
for (j in mdl_ls){
    dat <- prd_seldat(df=dfm, flux = "CH4", id_eq = j) # Select data
    dat <- na.omit(dat)
    par <- prd_gpar(id_eq = j, dfparam = mdlparls) # Select parameter
    colnames(dat) <- prd_prpdat(dat, resp_var = T)
    pCH4 <- getpred(df=dat, p=par, id_eq=j) # prep data and calc pred
    tp <- data.frame(CH4=dat$Y, mdl=j, pCH4=pCH4)
    prediction <- rbind(prediction,tp)
}
# compute residuals
prediction$pCH4_res <- (prediction$CH4-prediction$pCH4)
```

# Diagnostic plots {.tabset}

## CH4~a+IVcov*b

```{r, fig.height=4, eval=T}
dfs <- filter(prediction, mdl=="lin-IVcov")
a <- mdlpar[mdlpar$mdl == "lin-IVcov",]
round(a[,1:15], 3)
```

```{r, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
plt_mesmod(dfs$CH4, dfs$pCH4, mod_label = "modelled CH4", mes_label = "measured CH4",x_lim = c(0,0.2), y_lim = c(0,0.2))
plt_resmod(dfs$CH4, dfs$pCH4, x_lim = c(0,0.2))
par(mfrow=c(1,1))
```

```{r, fig.height=7, eval=T}
# par(mfrow=c(2,3))
# plot(dfs$pCH4_res~dfm$WTL, main="vs. WTL") 
# plot(dfs$pCH4_res~dfm$RH, main="vs. SWC") 
# plot(dfs$pCH4_res~dfm$IVcov, main="vs. IV cov")
# plot(dfs$pCH4_res~dfm$A, main="vs. A")
# plot(dfs$pCH4_res~dfm$H, main="vs. H")
# plot(dfs$pCH4_res~dfm$M, main="vs. M")
# plot(dfs$pCH4_res~dfm$NPOC, main="vs. NPOC")
# par(mfrow=c(1,1))
```
## CH4~aexp(bIVcov)

```{r, fig.height=4, eval=T}
dfs <- filter(prediction, mdl=="exp-IVcov")
a <- mdlpar[mdlpar$mdl == "exp-IVcov",]
round(a[,1:15], 3)
```

```{r, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
plt_mesmod(dfs$CH4, dfs$pCH4, mod_label = "modelled CH4", mes_label = "measured CH4",x_lim = c(0,0.2), y_lim = c(0,0.2))
plt_resmod(dfs$CH4, dfs$pCH4, x_lim = c(0,0.2))
par(mfrow=c(1,1))
```

```{r, fig.height=7, eval=T}
# par(mfrow=c(2,3))
# plot(dfs$pCH4_res~dfm$WTL, main="vs. WTL") 
# plot(dfs$pCH4_res~dfm$RH, main="vs. SWC") 
# plot(dfs$pCH4_res~dfm$IVcov, main="vs. IV cov")
# plot(dfs$pCH4_res~dfm$A, main="vs. A")
# plot(dfs$pCH4_res~dfm$H, main="vs. H")
# plot(dfs$pCH4_res~dfm$M, main="vs. M")
# plot(dfs$pCH4_res~dfm$NPOC, main="vs. NPOC")
# par(mfrow=c(1,1))
```

## CH4~aexp(bTair)

```{r, fig.height=4, eval=T}
dfs <- filter(prediction, mdl=="exp-Tair")
a <- mdlpar[mdlpar$mdl == "exp-Tair",]
round(a[,1:15], 3)
```

```{r, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
plt_mesmod(dfs$CH4, dfs$pCH4, mod_label = "modelled CH4", mes_label = "measured CH4",x_lim = c(0,0.2), y_lim = c(0,0.2))
plt_resmod(dfs$CH4, dfs$pCH4, x_lim = c(0,0.2))
par(mfrow=c(1,1))
```

```{r, fig.height=7, eval=T}
# par(mfrow=c(2,3))
# plot(dfs$pCH4_res~dfm$WTL, main="vs. WTL") 
# plot(dfs$pCH4_res~dfm$RH, main="vs. SWC") 
# plot(dfs$pCH4_res~dfm$IVcov, main="vs. IV cov")
# plot(dfs$pCH4_res~dfm$A, main="vs. A")
# plot(dfs$pCH4_res~dfm$H, main="vs. H")
# plot(dfs$pCH4_res~dfm$M, main="vs. M")
# plot(dfs$pCH4_res~dfm$NPOC, main="vs. NPOC")
# par(mfrow=c(1,1))
```


## CH4~aexp(bT40)

```{r, fig.height=4, eval=T}
dfs <- filter(prediction, mdl=="exp-T40")
a <- mdlpar[mdlpar$mdl == "exp-T40",]
round(a[,1:15], 3)
```

```{r, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
plt_mesmod(dfs$CH4, dfs$pCH4, mod_label = "modelled CH4", mes_label = "measured CH4",x_lim = c(0,0.2), y_lim = c(0,0.2))
plt_resmod(dfs$CH4, dfs$pCH4, x_lim = c(0,0.2))
par(mfrow=c(1,1))
```

```{r, fig.height=7, eval=T}
# par(mfrow=c(2,3))
# plot(dfs$pCH4_res~dfm$WTL, main="vs. WTL") 
# plot(dfs$pCH4_res~dfm$RH, main="vs. SWC") 
# plot(dfs$pCH4_res~dfm$IVcov, main="vs. IV cov")
# plot(dfs$pCH4_res~dfm$A, main="vs. A")
# plot(dfs$pCH4_res~dfm$H, main="vs. H")
# plot(dfs$pCH4_res~dfm$M, main="vs. M")
# plot(dfs$pCH4_res~dfm$NPOC, main="vs. NPOC")
# par(mfrow=c(1,1))
```

## CH4~aexp(bT80)

```{r, fig.height=4, eval=T}
dfs <- filter(prediction, mdl=="exp-T80")
a <- mdlpar[mdlpar$mdl == "exp-T80",]
round(a[,1:15], 3)
```

```{r, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
plt_mesmod(dfs$CH4, dfs$pCH4, mod_label = "modelled CH4", mes_label = "measured CH4",x_lim = c(0,0.2), y_lim = c(0,0.2))
plt_resmod(dfs$CH4, dfs$pCH4, x_lim = c(0,0.2))
par(mfrow=c(1,1))
```

```{r, fig.height=7, eval=T}
# par(mfrow=c(2,3))
# plot(dfs$pCH4_res~dfm$WTL, main="vs. WTL") 
# plot(dfs$pCH4_res~dfm$RH, main="vs. SWC") 
# plot(dfs$pCH4_res~dfm$IVcov, main="vs. IV cov")
# plot(dfs$pCH4_res~dfm$A, main="vs. A")
# plot(dfs$pCH4_res~dfm$H, main="vs. H")
# plot(dfs$pCH4_res~dfm$M, main="vs. M")
# plot(dfs$pCH4_res~dfm$NPOC, main="vs. NPOC")
# par(mfrow=c(1,1))
```

# Saves
```{r sav_mdl_par}
write.csv(mdlparls, file.path(outpath, "CH4_mdl_par.csv"), quote=F, row.names=F)
write.csv(prediction, file.path(outpath, "CH4_pred_cal.csv"), quote=F, row.names=F)
```

