---
title: "GPP calibration (avg/campaign)"
author: "Benoît D'ANGELO"
date: "14 avril 2016"
output:
  html_document:
    code_folding: hide
    fig_height: 3
    fig_width: 7
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../mod_toc.html"> Modélisation </a></h3>
***

# Objectives
This files describe the calibration of the GPP fluxes. This calibration is made in 2 steps, first the calibration using only flux data with light saturation (GPPsat). Then the ponderation with the light (GPP)

2 files are generated:

* GPPsatGPP_mdl_par.csv (contains models parameters for both GPPsat and GPP)
* GPPsatGPP_pred_cal.csv

# Setup

## Load packages and set paths

```{r ld_pckg, message=FALSE}
# File name : /2013_spavar_LG/report/modelisation/calibration/ER_perCampaign.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade packages (see "Howto" page to install them)
library(bdphdtoolbox)     # personnal toolbox

# CRAN packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)

# Folder to save graphes
savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance"

# Folder to save data treatement
outpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed"

# allow wider tables and graphes in html output
options(width = 100)
knitr::opts_chunk$set(fig.width=12,fig.height=8)

# Load custom color set
source("../../../src/report/custom_colors.R")
# source("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/src/report/custom_colors.R")
```

## Load functions

```{r ld_fn}
pGPP_T <- function(df, x_lab){
par(mar=c(5.1,5.1,2.1,2.1))
plot(Y~X, xlab=x_lab, ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=df)
# curve(a*exp(b*x), add=T, col="blue")
}

### models fonctions ------------------------------------------------

mdl_june <- function(df, start){
mdl <- nls(Y ~ a * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
}

mdl_linjune <- function(df, start){
mdl <- nls(Y ~ (a*X2 + d) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
}
# mdl_linjune <- function(df, start){
# mdl <- nls(Y ~ (a*X2) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
# }

mdl_linlinjune <- function(df, start){
mdl <- nls(Y ~ (a*X2 + d*X3) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude, trace=T)
}



mdl_param <- function(df, mdl){
  # R2
  devmean <- df$Y-(mean(df$Y)) # deviation à la moyenne
  SSres <-sum((resid(mdl))^2) # Total sum of squares
  SStot <- sum(devmean^2) # Residual sum of squares
  # 2 way to calculate
  # R2 <- (SStot-SSres)/SStot 
  R2 <- 1 - SSres/SStot
  # Adjusted R2
  N <- NROW(devmean) # sample size
  p <- 1 # number of predictors
  R2a <- 1-((1-R2)*(N-1))/(N-p-1)
  # RMSE
  rmse_mdl <- sqrt(mean(((predict(mdl))-df$Y)^2,na.rm=TRUE))
  nrmse_mdl <- 100*rmse_mdl/mean(df$Y)
  # Collect usefull param
  df <- data.frame(a=coef(mdl)[1],
                   b=coef(mdl)[2],
                   c=coef(mdl)[3],
                   d=coef(mdl)[4],
                   a_se=coef(summary(mdl))[,"Std. Error"][1],
                   b_se=coef(summary(mdl))[,"Std. Error"][2],
                   c_se=coef(summary(mdl))[,"Std. Error"][3],
                   d_se=coef(summary(mdl))[,"Std. Error"][4],
                   a_pval=coef(summary(mdl))[,"Pr(>|t|)"][1],
                   b_pval=coef(summary(mdl))[,"Pr(>|t|)"][2],
                   c_pval=coef(summary(mdl))[,"Pr(>|t|)"][3],
                   d_pval=coef(summary(mdl))[,"Pr(>|t|)"][4],
                   R2=R2,
                   aR2=R2a,
                   rmse=rmse_mdl,
                   nrmse=nrmse_mdl,
                   aic=AIC(mdl),
                   bic=BIC(mdl))
  return(df)
}


mdl_indic <- function(Y, pY, mdl){
  mdl <- unique(mdl)
  if(grepl("_", mdl)){
    p <- 2
  }else{ p <- 1}
  # R2
  devmean <- Y-(mean(Y, na.rm=TRUE)) # deviation à la moyenne
  SSres <-sum((Y-pY)^2) # Total sum of squares
  SStot <- sum(devmean^2) # Residual sum of squares
  # 2 way to calculate
  # R2 <- (SStot-SSres)/SStot 
  R2 <- 1 - SSres/SStot
  # Adjusted R2
  N <- NROW(devmean) # sample size
  # p <- 1 # number of predictors
  R2a <- 1-((1-R2)*(N-1))/(N-p-1)
  # RMSE
  rmse_mdl <- sqrt(mean((pY-Y)^2,na.rm=TRUE))
  nrmse_mdl <- 100*rmse_mdl/mean(Y,na.rm=TRUE)
  # Collect usefull param
  df <- data.frame(R2=R2,
                   aR2=R2a,
                   rmse=rmse_mdl,
                   nrmse=nrmse_mdl)
  return(df)
}
```


# GPPsat calibration

## Load and transform data

```{r ld_data}
# Load treated data (generated with getClean_fluxesFC)
# Campaign average
df <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC.csv")%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  filter(GPP > 0, PAR > 500) # FILTER to use only PAR saturation measurements 

# Averaging by campaign after filtering PAR > 500  ---------------------------------------------------
dfm_f <- df %>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  group_by(ID_camp)%>%
  summarise(
    GPP_sd = sd(GPP, na.rm=T),
    GPP = mean(GPP, na.rm=T),
    ER_sd = sd(ER, na.rm=T),
    ER = mean(ER, na.rm=T),
    NEE_sd = sd(NEE, na.rm=T),
    NEE = mean(NEE, na.rm=T),
    CH4_sd = sd(CH4, na.rm=T),
    CH4 = mean(CH4, na.rm=T),
    date=min(date, na.rm=T),
    timestamp=mean(timestamp, na.rm=T),
    Tair=mean(Tair, na.rm=T),
    TairS=mean(TairS, na.rm=T),
    T5S=mean(T5S, na.rm=T),
    T10S=mean(T10S, na.rm=T),
    T20S=mean(T20S, na.rm=T),
    T40S=mean(T40S, na.rm=T),
    T5=mean(T5, na.rm=T),
    T10=mean(T10, na.rm=T),
    T20=mean(T20, na.rm=T),
    T30=mean(T30, na.rm=T),
    T40=mean(T40, na.rm=T),
    T50=mean(T50, na.rm=T),
    T60=mean(T60, na.rm=T),
    T70=mean(T70, na.rm=T),
    T80=mean(T80, na.rm=T),
    T90=mean(T90, na.rm=T),
    T100=mean(T100, na.rm=T),
    IVcov=mean(IVcov, na.rm=T),
    A=mean(A, na.rm=T),
    H=mean(H, na.rm=T),
    M=mean(M, na.rm=T),
    RH=mean(RH, na.rm=T),
    NPOC=mean(NPOC, na.rm=T),
    WTL=mean(WTL, na.rm=T)
  )%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))
```

## GPPsat models calculations

```{r mdl_calc}
# Non linear version --------------------
# Tair june
dmdl_1 <- dfm_f %>%
  rename(Y=GPP, X=Tair)%>%
  select(Y, X, WTL, RH, IVcov, A, H, M)
mdl_1 <- mdl_june(dmdl_1, list(a=20, b=50, c=20))
par_1 <- mdl_param(dmdl_1, mdl_1)

# T5 june
dmdl_2 <- dfm_f %>%
  rename(Y=GPP, X=T5)%>%
  select(Y, X, WTL, RH, IVcov, A, H, M)
mdl_2 <- mdl_june(dmdl_2, list(a=10, b=10, c=10))
par_2 <- mdl_param(dmdl_2, mdl_2)

# Tair + IVcov june
dmdl_1_1 <- dfm_f %>%
  rename(Y=GPP, X=Tair, X2=IVcov)%>%
  select(Y, X, X2, WTL, RH, A, H, M)
mdl_1_1 <- mdl_linjune(dmdl_1_1, list(a=20, b=40, c=20, d=1))
par_1_1 <- mdl_param(dmdl_1_1, mdl_1_1)

# Tair + H june
dmdl_1_2 <- dfm_f %>%
  rename(Y=GPP, X=Tair, X2=H)%>%
  select(Y, X, X2, WTL, RH, IVcov, A, M)
mdl_1_2 <- mdl_linjune(dmdl_1_2, list(a=20, b=40, c=20, d=1))
par_1_2 <- mdl_param(dmdl_1_2, mdl_1_2)

# Tair + A june
dmdl_1_3 <- dfm_f %>%
  rename(Y=GPP, X=Tair, X2=A)%>%
  select(Y, X, X2, WTL, RH, IVcov, H, M)
mdl_1_3 <- mdl_linjune(dmdl_1_3, list(a=20, b=40, c=20, d=1))
par_1_3 <- mdl_param(dmdl_1_3, mdl_1_3)

# T5 + IVcov june
dmdl_2_1 <- dfm_f %>%
  rename(Y=GPP, X=T5, X2=IVcov)%>%
  select(Y, X, X2, WTL, RH, A, H, M)
mdl_2_1 <- mdl_linjune(dmdl_2_1, list(a=10, b=10, c=10, d=1))
par_2_1 <- mdl_param(dmdl_2_1, mdl_2_1)

# T5 + H june
dmdl_2_2 <- dfm_f %>%
  rename(Y=GPP, X=T5, X2=H)%>%
  select(Y, X, X2, WTL, RH, IVcov, A, M)
mdl_2_2 <- mdl_linjune(dmdl_2_2, list(a=10, b=10, c=10, d=1))
par_2_2 <- mdl_param(dmdl_2_2, mdl_2_2)

# dmdl_1_1_1 <- df %>%
#   rename(Y=GPP, X=T5, X2=IVcov, X3=RH)%>%
#   select(Y, X, X2, X3, WTL)
# mdl_1_1_1 <- mdl_linlinjune(dmdl_1_1_1, list(a=30, b=50, c=20, d=20))
# par_1_1_1 <- mdl_param(dmdl_1_1_1, mdl_1_1_1)

# dmdl_2_1_1 <- df %>%
#   rename(Y=GPP, X=T5, X2=IVcov, X3=RH)%>%
#   select(Y, X, X2, X3, WTL)
# mdl_2_1_1 <- mdl_linlinexp(dmdl_2_1_1)
# par_2_1_1 <- mdl_param(dmdl_2_1_1, mdl_2_1_1)

```

##  Models output

```{r mdl_output}
mdlls <- c("exp-Tair", "exp-T5", "exp-Tair_IVcov", "exp-Tair_H", "exp-Tair_A", "exp-T5_IVcov", "exp-T5_H")

par <- c(par_1, par_2, par_1_1, par_1_2, par_1_3, par_2_1, par_2_2)
mdlpar <- data.frame(matrix(unlist(par), nrow=length(mdlls), byrow=T))
colnames(mdlpar) <- c("a", "b", "c", "d","a_se", "b_se", "c_se", "d_se", "a_pval", "b_pval", "c_pval", "d_pval", "R2", "R2a", "rmse", "nrmse", "aic", "bic")

res <- data.frame(mdl=mdlls)
res <- cbind(res, mdlpar)

not <- data.frame(hglgt = c("<-","","<-","<-","","",""))

best <- cbind(res, not)%>%
  filter(hglgt == "<-")

result <- res
result[,-1] <- round(result[,-1],2) # round sauf 1re col
result <- cbind(result, not)
```

### Models sort by R2a

```{r}
result %>%
  select(mdl, R2, R2a, rmse, nrmse, aic, bic, hglgt)%>%
  arrange(desc(R2a))
```

### Models parameters

```{r}
result %>%
  select(mdl, a, b, c, d, a_se, b_se, c_se, d_se, a_pval, b_pval, c_pval, d_pval)
```

## GPPsat diagnostic plots {.tabset}

### GPP~aexp-((Tair-b)/c)

```{r, fig.height=4, eval=T}
par_1
par(mfrow=c(1,3))
pGPP_T(dmdl_1, "température de l'air cm (°C)")
curve(par_1$a*exp(-((x-par_1$b)/par_1$c)^2), add=T, col="blue")
plt_mesmod(dmdl_1$Y, predict(mdl_1), mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dmdl_1$Y, predict(mdl_1))
par(mfrow=c(1,1))

```
```{r, fig.height=7, eval=T}
par(mfrow=c(2,3))
plot(resid(mdl_1)~dmdl_1$WTL, main="vs. WTL") 
plot(resid(mdl_1)~dmdl_1$RH, main="vs. RH") 
plot(resid(mdl_1)~dmdl_1$IVcov, main="vs. IV cov")
plot(resid(mdl_1)~dmdl_1$A, main="vs. A")
plot(resid(mdl_1)~dmdl_1$H, main="vs. H")
plot(resid(mdl_1)~dmdl_1$M, main="vs. M")
par(mfrow=c(1,1))
```

### GPP~aexp-((T5-b)/c)

```{r, fig.height=4}
par_2
par(mfrow=c(1,3))
pGPP_T(dmdl_2, "température de la tourbe à -5 cm (°C)")
curve(par_2$a*exp(-((x-par_2$b)/par_2$c)^2), add=T, col="blue")
plt_mesmod(dmdl_2$Y, predict(mdl_2), mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dmdl_2$Y, predict(mdl_2))
par(mfrow=c(1,1))

# par(mfrow=c(1,3))
# plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_2$RH, main="vs. RH") 
# plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
# par(mfrow=c(1,1))
```
```{r, fig.height=7}
par(mfrow=c(2,3))
plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
plot(resid(mdl_2)~dmdl_2$RH, main="vs. RH") 
plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
plot(resid(mdl_2)~dmdl_2$A, main="vs. A")
plot(resid(mdl_2)~dmdl_2$H, main="vs. H")
plot(resid(mdl_2)~dmdl_2$M, main="vs. M")
par(mfrow=c(1,1))
```


### GPP~(a*H) * exp-((Tair-b)/c)

```{r, fig.height=4, eval=T}
par_1_2
par(mfrow=c(1,3))
pGPP_T(dmdl_1_2, "température de l'air (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
plt_mesmod(dmdl_1_2$Y, predict(mdl_1_2), mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dmdl_1_2$Y, predict(mdl_1_2))
par(mfrow=c(1,1))

```

### GPP~(a*IVcov) * exp-((Tair-b)/c)

```{r, fig.height=4, eval=T}
par_1_1
par(mfrow=c(1,3))
pGPP_T(dmdl_1_1, "température de l'air (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
plt_mesmod(dmdl_1_1$Y, predict(mdl_1_1), mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dmdl_1_1$Y, predict(mdl_1_1))
par(mfrow=c(1,1))

# par(mfrow=c(1,3))
# plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_2$RH, main="vs. RH") 
# plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
# par(mfrow=c(1,1))
```

### GPP~(a*H) * exp-((T5-b)/c)

```{r, fig.height=4, eval=T}
par_2_2
par(mfrow=c(1,3))
pGPP_T(dmdl_2_2, "température de la tourbe à -5 cm (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
plt_mesmod(dmdl_2_2$Y, predict(mdl_2_2), mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dmdl_2_2$Y, predict(mdl_2_2))
par(mfrow=c(1,1))
```

### GPP~(a*IVcov) * exp-((T5-b)/c)

```{r, fig.height=4}
par_2_1
par(mfrow=c(1,3))
pGPP_T(dmdl_2_1, "température de la tourbe à -5 cm (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
plt_mesmod(dmdl_2_1$Y, predict(mdl_2_1), mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dmdl_2_1$Y, predict(mdl_2_1))
par(mfrow=c(1,1))
```

# GPP calibration

## Load and transform data

```{r}
# /!\ 2 versions /!\
# VERSION 1 : Données moyennées sans retrait des NA au préalable
# Load treated data (generated with getClean_fluxesFC)
# Campaign average
# dfm <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC_avg.csv")%>%
#   mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
#   mutate(date=as.POSIXct(as.character(date)))%>%
#   select(date, GPP, PAR, Tair, T5, IVcov, H, RH)

# VERSION 2 (thèse) : Données moyennées après retrait des NA
df <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC.csv")%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  select(placette, date, ID_camp, ER, GPP, NEE, Tair, T5, WTL, PAR, RH, H, IVcov, IVcov_area)%>%
  do(na.omit(.)) # Ligne qui fait la différence entre les deux versions

dfm <- df %>%
  group_by(ID_camp)%>%
  summarise(date=min(date, na.rm=T),
            GPP=mean(GPP, na.rm=T),
            PAR=mean(PAR, na.rm=T),
            Tair=mean(Tair, na.rm=T),
            T5=mean(T5, na.rm=T),
            PAR=mean(PAR, na.rm=T),
            WTL=mean(WTL, na.rm=T),
            RH=mean(RH, na.rm=T),
            H=mean(H, na.rm=T),
            IVcov=mean(IVcov, na.rm=T),
            IVcov_area=mean(IVcov_area, na.rm=T)
            )
dfm <- as.data.frame(dfm)

# /!\ 2 versions /!\
# Résultats légèrement différent de ceux de la thèse car pour cette dernière j'avais enlevé toutes les lignes contenant des NA sur les variables qui m'intéressait avant de faire les moyennes (do(na.omit(.)))...
```

## GPP calculations

```{r, message=FALSE}
# Get models parameters
GPPsatpar <- res %>%
  select(mdl, a, b, c, d)

# GPPsatpar$mdl <- paste0("exp-", GPPsatpar$mdl)

mdl_list <- c("exp-Tair", "exp-T5", "exp-Tair_H", "exp-Tair_IVcov", "exp-T5_IVcov")

GPPpred <- data.frame()
# predGPP <- data.frame()
GPPpar <- data.frame()
for (j in mdl_list){
    # Setup
    dat <- prd_seldat(df=dfm, flux = "GPP", id_eq = j) # Select data
    par <- prd_gpar(id_eq = j, dfparam = GPPsatpar) # Select parameter
    colnames(dat) <- prd_prpdat(dat, resp_var = T)
    # GPPsat calc
    pGPPsat <- gpGPPsat(df=dat, p=par) # prep data and calc pred
    # GPP calc
    m <- nls(GPP ~ a*PAR*pGPPsat/(pGPPsat+PAR*a),
                 data=dfm,
                 start=list(a=0.005))
    i <- coef(m)[1] # par
    # pGPP = (i*dfm$PAR*pGPPsat/(sqrt(pGPPsat^2+(dfm$PAR*i)^2)))
    pGPP = (i*dfm$PAR*pGPPsat/(pGPPsat+dfm$PAR*i))
    indic <- data.frame(mdl=j, i=i, AIC=AIC(m), BIC=BIC(m),
                      a_se=coef(summary(m))[,"Std. Error"][1], 
                      a_pval=coef(summary(m))[,"Pr(>|t|)"][1])
    
    # Output
    ## GPPsat
    tpGPPsat <- data.frame(GPP=dfm$GPP, mdl=j, pGPPsat=pGPPsat, pGPP=pGPP)
    GPPpred <- rbind(GPPpred,tpGPPsat) 
    GPPpar <- rbind(GPPpar, indic) # modelGPPpar
}

GPPpar$mdl <- as.character(GPPpar$mdl)
GPPpred$mdl <- as.character(GPPpred$mdl)

# all parameter values from models
allpar <- full_join(GPPsatpar, GPPpar[,1:2])

# Export paramètre mdl GPP
write.csv(allpar, file.path(outpth, "GPPsatGPP_mdl_par.csv"), quote=F, row.names=F)
# Save GPP prediction
write.csv(GPPpred, file.path(outpth, "GPPsatGPP_pred_cal.csv"), quote=F, row.names=F)
```

## Model output

### GPP models (quality indicator and parameter)

```{r, message=F}
GPPind <- GPPpar
# Tableau resultats modèles
ldf <- GPPpred %>%
  group_by(mdl)%>%
  do(mdl_indic(.$GPP, .$pGPP, mdl=.$mdl))%>%
  ungroup()%>%
  inner_join(., GPPind)%>%
  arrange(desc(aR2))

ldf[,2:10] <- round(ldf[,2:10], 2)
ldf
```

## GPP diagnostic plots {.tabset}

### Tair

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "exp-Tair")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
```

### Tair + IVcov

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "exp-Tair_IVcov")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
```

### T5

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "exp-T5")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
iT5 <- mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
iT5
```

### T5 + IVcov

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "exp-T5_IVcov")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
plt_resmod(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
iT5_IV <- mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
iT5_IV
```