---
title: "GPP calibration (avg/campaign)"
author: "Benoît D'ANGELO"
date: "14 avril 2016"
output:
  html_document:
    code_folding: hide
    fig_height: 3
    fig_width: 7
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../mod_toc.html"> Calibration </a></h3>
***

# Objectives
This files describe the calibration of the GPP fluxes. One file is generated:

* GPPsat_mdlpar.csv (contains models parameters)
* GPP_mdlpar.csv

# Setup

## Load packages and set paths

```{r ld_pckg, message=FALSE}
# File name : /2013_spavar_LG/report/modelisation/calibration/ER_perCampaign.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade packages (see "Howto" page to install them)
library(bdphdtoolbox)     # personnal toolbox

# CRAN packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)

# Folder to save graphes
savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance"

# Folder to save data treatement
outpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed"

# allow wider tables and graphes in html output
options(width = 100)
knitr::opts_chunk$set(fig.width=12,fig.height=8)

# Load custom color set
source("../../../src/report/custom_colors.R")
# source("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/src/report/custom_colors.R")
```

## Load functions

```{r ld_fn}
pGPP_T <- function(df, x_lab){
par(mar=c(5.1,5.1,2.1,2.1))
plot(Y~X, xlab=x_lab, ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=df)
# curve(a*exp(b*x), add=T, col="blue")
}

# pGPP_Tair <- function(X){
# par(mar=c(5.1,5.1,2.1,2.1))
# plot(GPP~Tair, xlab="température de l'air (°C)",ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# # curve(a*exp(b*x), add=T, col="blue")
# }

pmesmod <- function(df, mdl){
par(mar=c(4,4.5,.5,.5))
plot(Y~predict(mdl), 
     ylim=c(1,14), xlim=c(1,14),
     xlab="", ylab="", data=df)
title(xlab=expression(paste("PBB modélisée (", mu, mol,m^-2,s^-1,")", sep="")), line=2.5)
title(ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
abline(a=0, b=1, col="black", lty=2)
text(19,20, "1:1", srt=45)
}

presmod <- function(mdl){
par(mar=c(4,4,.5,.5))
plot(resid(mdl)~predict(mdl))
title(xlab="valeurs prédites", line=2.5)
title(ylab="résidus", line=2)
}

### models fonctions ------------------------------------------------

mdl_june <- function(df, start){
mdl <- nls(Y ~ a * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
}

mdl_linjune <- function(df, start){
mdl <- nls(Y ~ (a*X2 + d) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
}
# mdl_linjune <- function(df, start){
# mdl <- nls(Y ~ (a*X2) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
# }

mdl_linlinjune <- function(df, start){
mdl <- nls(Y ~ (a*X2 + d*X3) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude, trace=T)
}

mdl_param <- function(df, mdl){
  # R2
  devmean <- df$Y-(mean(df$Y)) # deviation à la moyenne
  SSres <-sum((resid(mdl))^2) # Total sum of squares
  SStot <- sum(devmean^2) # Residual sum of squares
  # 2 way to calculate
  # R2 <- (SStot-SSres)/SStot 
  R2 <- 1 - SSres/SStot
  # Adjusted R2
  N <- NROW(devmean) # sample size
  p <- 1 # number of predictors
  R2a <- 1-((1-R2)*(N-1))/(N-p-1)
  # RMSE
  rmse_mdl <- sqrt(mean(((predict(mdl))-df$Y)^2,na.rm=TRUE))
  nrmse_mdl <- 100*rmse_mdl/mean(df$Y)
  # Collect usefull param
  df <- data.frame(a=coef(mdl)[1],
                   b=coef(mdl)[2],
                   c=coef(mdl)[3],
                   d=coef(mdl)[4],
                   a_se=coef(summary(mdl))[,"Std. Error"][1],
                   b_se=coef(summary(mdl))[,"Std. Error"][2],
                   c_se=coef(summary(mdl))[,"Std. Error"][3],
                   d_se=coef(summary(mdl))[,"Std. Error"][4],
                   a_pval=coef(summary(mdl))[,"Pr(>|t|)"][1],
                   b_pval=coef(summary(mdl))[,"Pr(>|t|)"][2],
                   c_pval=coef(summary(mdl))[,"Pr(>|t|)"][3],
                   d_pval=coef(summary(mdl))[,"Pr(>|t|)"][4],
                   R2=R2,
                   aR2=R2a,
                   rmse=rmse_mdl,
                   nrmse=nrmse_mdl,
                   aic=AIC(mdl),
                   bic=BIC(mdl))
  return(df)
}
```


## Load and transform data

```{r ld_data}
# Load treated data (generated with getClean_fluxesFC)
# Campaign average
df <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC.csv")%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  filter(GPP > 0, PAR > 500) # FILTER to use only PAR saturation measurements 

# Averaging by campaign ---------------------------------------------------
dfm <- df %>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  group_by(ID_camp)%>%
  summarise(
    GPP_sd = sd(GPP, na.rm=T),
    GPP = mean(GPP, na.rm=T),
    ER_sd = sd(ER, na.rm=T),
    ER = mean(ER, na.rm=T),
    NEE_sd = sd(NEE, na.rm=T),
    NEE = mean(NEE, na.rm=T),
    CH4_sd = sd(CH4, na.rm=T),
    CH4 = mean(CH4, na.rm=T),
    date=min(date, na.rm=T),
    timestamp=mean(timestamp, na.rm=T),
    Tair=mean(Tair, na.rm=T),
    TairS=mean(TairS, na.rm=T),
    T5S=mean(T5S, na.rm=T),
    T10S=mean(T10S, na.rm=T),
    T20S=mean(T20S, na.rm=T),
    T40S=mean(T40S, na.rm=T),
    T5=mean(T5, na.rm=T),
    T10=mean(T10, na.rm=T),
    T20=mean(T20, na.rm=T),
    T30=mean(T30, na.rm=T),
    T40=mean(T40, na.rm=T),
    T50=mean(T50, na.rm=T),
    T60=mean(T60, na.rm=T),
    T70=mean(T70, na.rm=T),
    T80=mean(T80, na.rm=T),
    T90=mean(T90, na.rm=T),
    T100=mean(T100, na.rm=T),
    IVcov=mean(IVcov, na.rm=T),
    A=mean(A, na.rm=T),
    H=mean(H, na.rm=T),
    M=mean(M, na.rm=T),
    RH_m=mean(RH_m, na.rm=T),
    NPOC=mean(NPOC, na.rm=T),
    WTL=mean(WTL, na.rm=T)
  )%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))
```

# Calculations
```{r mdl_calc}
# Non linear version --------------------
# Tair june
dmdl_1 <- dfm %>%
  rename(Y=GPP, X=Tair)%>%
  select(Y, X, WTL, RH_m, IVcov, A, H, M)
mdl_1 <- mdl_june(dmdl_1, list(a=20, b=50, c=20))
par_1 <- mdl_param(dmdl_1, mdl_1)

# T5 june
dmdl_2 <- dfm %>%
  rename(Y=GPP, X=T5)%>%
  select(Y, X, WTL, RH_m, IVcov, A, H, M)
mdl_2 <- mdl_june(dmdl_2, list(a=10, b=10, c=10))
par_2 <- mdl_param(dmdl_2, mdl_2)

# Tair + IVcov june
dmdl_1_1 <- dfm %>%
  rename(Y=GPP, X=Tair, X2=IVcov)%>%
  select(Y, X, X2, WTL, RH_m, A, H, M)
mdl_1_1 <- mdl_linjune(dmdl_1_1, list(a=20, b=40, c=20, d=1))
par_1_1 <- mdl_param(dmdl_1_1, mdl_1_1)

# Tair + H june
dmdl_1_2 <- dfm %>%
  rename(Y=GPP, X=Tair, X2=H)%>%
  select(Y, X, X2, WTL, RH_m, IVcov, A, M)
mdl_1_2 <- mdl_linjune(dmdl_1_2, list(a=20, b=40, c=20, d=1))
par_1_2 <- mdl_param(dmdl_1_2, mdl_1_2)

# Tair + A june
dmdl_1_3 <- dfm %>%
  rename(Y=GPP, X=Tair, X2=A)%>%
  select(Y, X, X2, WTL, RH_m, IVcov, H, M)
mdl_1_3 <- mdl_linjune(dmdl_1_3, list(a=20, b=40, c=20, d=1))
par_1_3 <- mdl_param(dmdl_1_3, mdl_1_3)

# T5 + IVcov june
dmdl_2_1 <- dfm %>%
  rename(Y=GPP, X=T5, X2=IVcov)%>%
  select(Y, X, X2, WTL, RH_m, A, H, M)
mdl_2_1 <- mdl_linjune(dmdl_2_1, list(a=10, b=10, c=10, d=1))
par_2_1 <- mdl_param(dmdl_2_1, mdl_2_1)

# T5 + H june
dmdl_2_2 <- dfm %>%
  rename(Y=GPP, X=T5, X2=H)%>%
  select(Y, X, X2, WTL, RH_m, IVcov, A, M)
mdl_2_2 <- mdl_linjune(dmdl_2_2, list(a=10, b=10, c=10, d=1))
par_2_2 <- mdl_param(dmdl_2_2, mdl_2_2)

# dmdl_1_1_1 <- df %>%
#   rename(Y=GPP, X=T5, X2=IVcov, X3=RH_m)%>%
#   select(Y, X, X2, X3, WTL)
# mdl_1_1_1 <- mdl_linlinjune(dmdl_1_1_1, list(a=30, b=50, c=20, d=20))
# par_1_1_1 <- mdl_param(dmdl_1_1_1, mdl_1_1_1)

# dmdl_2_1_1 <- df %>%
#   rename(Y=GPP, X=T5, X2=IVcov, X3=RH_m)%>%
#   select(Y, X, X2, X3, WTL)
# mdl_2_1_1 <- mdl_linlinexp(dmdl_2_1_1)
# par_2_1_1 <- mdl_param(dmdl_2_1_1, mdl_2_1_1)

```

```{r mdl_output}
mdlls <- c("Tair", "T5", "Tair_IVcov", "Tair_H", "Tair_A", "T5_IVcov", "jT5_H")

par <- c(par_1, par_2, par_1_1, par_1_2, par_1_3, par_2_1, par_2_2)
mdlpar <- data.frame(matrix(unlist(par), nrow=length(mdlls), byrow=T))
colnames(mdlpar) <- c("a", "b", "c", "d","a_se", "b_se", "c_se", "d_se", "a_pval", "b_pval", "c_pval", "d_pval", "R2", "R2a", "rmse", "nrmse", "aic", "bic")

res <- data.frame(mdl=mdlls)
res <- cbind(res, mdlpar)

not <- data.frame(best = c("<-","","<-","<-","","",""))

best <- cbind(res, not)%>%
  filter(best == "<-")

result <- res
result[,-1] <- round(result[,-1],2) # round sauf 1re col
result <- cbind(result, not)
```

## Models

```{r}
result
```

## Models sort by R2a

```{r}
result %>%
  select(mdl, R2, R2a, rmse, nrmse, aic, bic, best)%>%
  arrange(desc(R2a))

result %>%
  select(mdl, a, b, c, d, a_se, b_se, c_se, d_se, a_pval, b_pval, c_pval, d_pval)
```

# Diagnostic plots {.tabset}

## GPP~aexp-((Tair-b)/c)

```{r, fig.height=4, eval=T}
par_1
par(mfrow=c(1,3))
pGPP_T(dmdl_1, "température de l'air cm (°C)")
curve(par_1$a*exp(-((x-par_1$b)/par_1$c)^2), add=T, col="blue")
pmesmod(dmdl_1, mdl_1)
presmod(mdl_1)
par(mfrow=c(1,1))

```
```{r, fig.height=7, eval=T}
par(mfrow=c(2,3))
plot(resid(mdl_1)~dmdl_1$WTL, main="vs. WTL") 
plot(resid(mdl_1)~dmdl_1$RH_m, main="vs. RH") 
plot(resid(mdl_1)~dmdl_1$IVcov, main="vs. IV cov")
plot(resid(mdl_1)~dmdl_1$A, main="vs. A")
plot(resid(mdl_1)~dmdl_1$H, main="vs. H")
plot(resid(mdl_1)~dmdl_1$M, main="vs. M")
par(mfrow=c(1,1))
```

## GPP~aexp-((T5-b)/c)

```{r, fig.height=4}
par_2
par(mfrow=c(1,3))
pGPP_T(dmdl_2, "température de la tourbe à -5 cm (°C)")
curve(par_2$a*exp(-((x-par_2$b)/par_2$c)^2), add=T, col="blue")
pmesmod(dmdl_2, mdl_2)
presmod(mdl_2)
par(mfrow=c(1,1))

# par(mfrow=c(1,3))
# plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_2$RH_m, main="vs. RH") 
# plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
# par(mfrow=c(1,1))
```
```{r, fig.height=7}
par(mfrow=c(2,3))
plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
plot(resid(mdl_2)~dmdl_2$RH_m, main="vs. RH") 
plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
plot(resid(mdl_2)~dmdl_2$A, main="vs. A")
plot(resid(mdl_2)~dmdl_2$H, main="vs. H")
plot(resid(mdl_2)~dmdl_2$M, main="vs. M")
par(mfrow=c(1,1))
```


## GPP~(a*H) * exp-((Tair-b)/c)

```{r, fig.height=4, eval=FALSE}
par_1_2
par(mfrow=c(1,3))
pGPP_T(dmdl_1_2, "température de l'air (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
pmesmod(dmdl_1_2, mdl_1_2)
presmod(mdl_1_2)
par(mfrow=c(1,1))

```

## GPP~(a*IVcov) * exp-((Tair-b)/c)

```{r, fig.height=4, eval=T}
par_1_1
par(mfrow=c(1,3))
pGPP_T(dmdl_1_1, "température de l'air (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
pmesmod(dmdl_1_1, mdl_1_1)
presmod(mdl_1_1)
par(mfrow=c(1,1))

# par(mfrow=c(1,3))
# plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_2$RH_m, main="vs. RH") 
# plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
# par(mfrow=c(1,1))
```

## GPP~(a*H) * exp-((T5-b)/c)

```{r, fig.height=4, eval=FALSE}
par_2_2
par(mfrow=c(1,3))
pGPP_T(dmdl_2_2, "température de la tourbe à -5 cm (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
pmesmod(dmdl_2_2, mdl_2_2)
presmod(mdl_2_2)
par(mfrow=c(1,1))
```

## GPP~(a*IVcov) * exp-((T5-b)/c)

```{r, fig.height=4}
par_2_1
par(mfrow=c(1,3))
pGPP_T(dmdl_2_1, "température de la tourbe à -5 cm (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
pmesmod(dmdl_2_1, mdl_2_1)
presmod(mdl_2_1)
par(mfrow=c(1,1))
```

# Figures

```{r, fig.height=8}
labpar_1 <- format(par_1,  digits=2, nsmall=2)
labpar_1_1 <- format(par_1_1,  digits=2, nsmall=2)
labpar_2 <- format(par_2,  digits=2, nsmall=2)
labpar_1_2 <- format(par_1_2,  digits=2, nsmall=2)
labpar_2_1 <- format(par_2_1,  digits=2, nsmall=2)
# labpar_2_3 <- format(par_2_3,  digits=2, nsmall=2)


lab11 <- paste(
  "y = ", labpar_1$a, " * exp(", labpar_1$b, "*Tair)",
  "\nR² = ", labpar_1$aR2, 
  "\nRMSE = ", labpar_1$rmse,
  "\nNRMSE = ", labpar_1$nrmse, " %", sep="")
lab11_1 <- paste(
  "y = ", labpar_1_1$a, " * IV + ", labpar_1_1$c ,"exp(", labpar_1_1$b, "*Tair)",
  "\nR² = ", labpar_1_1$aR2, 
  "\nRMSE = ", labpar_1_1$rmse,
  "\nNRMSE = ", labpar_1_1$nrmse, " %", sep="")
lab21 <- paste0(
  "y = ", labpar_2$a, " * exp(", labpar_2$b, "*T5)",
  "\nR² = ", labpar_2$aR2, 
  "\nRMSE = ", labpar_2$rmse,
  "\nNRMSE = ", labpar_2$nrmse, " %", sep="")
lab21_1 <- paste(
  "y = ", labpar_2_1$a, " * IV + ", labpar_2_1$c ,"exp(", labpar_2_1$b, "*Tair)",
  "\nR² = ", labpar_2_1$aR2, 
  "\nRMSE = ", labpar_2_1$rmse,
  "\nNRMSE = ", labpar_2_1$nrmse, " %", sep="")

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_T5_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
pmesmod(dmdl_2, mdl_2)
text(x=.4, y=12, labels=lab21, adj=0)
plot(resid(mdl_2)~predict(mdl_2), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_T5IV_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
pmesmod(dmdl_2_1, mdl_2_1)
text(x=.4, y=12, labels=lab21_1, adj=0)
plot(resid(mdl_2_1)~predict(mdl_2_1), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))
# 
cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_T5_mdl_res.pdf"), width=5, height=4)
par(mfrow=c(1,1), mar=c(4,4.5,.5,.5))
# plot(resid(mdl_2)~dmdl_1$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_1$RH, main="vs. RH") 
plot(resid(mdl_2)~dmdl_2$IVcov,
     xlab="indice de végétation",
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep=""))) 
par(mfrow=c(1,1))

##################### Tair


cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_Tair_mesmod.pdf"), width=9, height=8)
par(mfrow=c(2,2))
## haut gauche
pmesmod(dmdl_1, mdl_1)
text(x=1, y=12.5, labels=lab11, adj=0)
text(x=13, y=2, labels="a", adj=0, cex=2)

## haut droite
plot(resid(mdl_1)~predict(mdl_1), xlab="", ylab="")
title(xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")), line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=13, y=-4, labels="b", adj=0, cex=2)

## bas gauche
plot(resid(mdl_1)~dmdl_1$IVcov, xlab="", ylab="") 
title(xlab="indice de végétation", line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=.5, y=-4, labels="c", adj=0, cex=2)

## bas droite
plot(resid(mdl_1)~dmdl_1$WTL, xlab="", ylab="") 
title(xlab="Niveau de la nappe (cm)", line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=17, y=-4, labels="d", adj=0, cex=2)

par(mfrow=c(1,1))

##################$ TairIVcov

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_TairIV_mesmod.pdf"), width=9, height=4)
par(mfrow=c(1,2))
## haut gauche
pmesmod(dmdl_1_1, mdl_1_1)
text(x=1, y=12.5, labels=lab11_1, adj=0)
text(x=13, y=2, labels="a", adj=0, cex=2)

## haut droite
plot(resid(mdl_1_1)~predict(mdl_1_1), xlab="", ylab="")
title(xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")), line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=12.3, y=-1.65, labels="b", adj=0, cex=2)

## bas gauche
# plot(resid(mdl_1_1)~dmdl_1_1$IVcov, xlab="", ylab="") 
# title(xlab="indice de végétation", line=2.5)
# title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
# text(x=.5, y=-4, labels="c", adj=0, cex=2)
# 
# ## bas droite
# plot(resid(mdl_1_1)~dmdl_1_1$WTL, xlab="", ylab="") 
# title(xlab="Niveau de la nappe (cm)", line=2.5)
# title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
# text(x=17, y=-4, labels="d", adj=0, cex=2)

par(mfrow=c(1,1))




cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_Tair_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
pmesmod(dmdl_1, mdl_1)
text(x=.4, y=12, labels=lab11, adj=0)
plot(resid(mdl_1)~predict(mdl_1), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_TairIV_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
pmesmod(dmdl_1_1, mdl_1_1)
text(x=.4, y=12, labels=lab11_1, adj=0)
plot(resid(mdl_1_1)~predict(mdl_1_1), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))
# 
cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_Tair_mdl_res.pdf"), width=5, height=4)
par(mfrow=c(1,1), mar=c(4,4.5,.5,.5))
# plot(resid(mdl_2)~dmdl_1$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_1$RH, main="vs. RH") 
plot(resid(mdl_1)~dmdl_1$IVcov,
     xlab="indice de végétation",
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep=""))) 
par(mfrow=c(1,1))
# 
# 
# cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance", "PPB_1par_mdl_res.pdf"), width=10, height=8)
# par(mfrow=c(2,2))
# pmesmod(dmdl_1, mdl_1)
# text(x=1, y=8, labels=lab11, adj=0)
# plot(resid(mdl_1)~dmdl_1$H, main="vs. H") 
# pmesmod(dmdl_2, mdl_2)
# text(x=1, y=8, labels=lab21, adj=0)
# plot(resid(mdl_2)~dmdl_1$RH_m, main="vs. TES") 
# par(mfrow=c(1,1))
# 
# lab11 <- paste(
#   "y = (", labpar_1_2$a, " * H + ", labpar_1_2$c, ") * exp(", labpar_1_2$b, "*Tair)",
#   "\nR² = ", labpar_1_2$aR2, 
#   "\nNRMSE = ", labpar_1_2$nrmse, sep="")
# # lab21 <- paste0(
# #   "y = (", labpar_2_3$a, " * TES + ", labpar_2_3$c, ") * exp(", labpar_2_3$b, "*T5)",
# #   "\nR² = ", labpar_2_3$aR2, 
# #   "\nNRMSE = ", labpar_2_3$nrmse)
# # 
# cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance", "PPB_2par_mdl.pdf"), width=5, height=4)
# par(mfrow=c(1,1))
# pmesmod(dmdl_1_2, mdl_1_2)
# text(x=1, y=8, labels=lab11, adj=0)
# # plot(resid(mdl_1)~dmdl_1$H, main="vs. H") 
# # pmesmod(dmdl_2_3, mdl_2_3)
# # text(x=1, y=18, labels=lab21, adj=0)
# # # plot(resid(mdl_2)~dmdl_1$RH_m, main="vs. TES") 
# par(mfrow=c(1,1))

```

# Data
```{r sav_mdl_par}
select(best, -best)

export <- res %>%
  select(mdl, a, b, c, d)

filepath_mdl <- paste0(outpth, "/GPPsat_mdlpar.csv")
write.csv(export, filepath_mdl, quote=F, row.names=F)
```



# Non sat

TODO put cb_GPP_avg_2.Rmd there
