---
title: "GPP calibration (avg/campaign)"
author: "Benoît D'ANGELO"
date: "14 avril 2016"
output:
  html_document:
    code_folding: hide
    fig_height: 3
    fig_width: 7
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../mod_toc.html"> Calibration </a></h3>
***

# Objectives
This files describe the calibration of the GPP fluxes. One file is generated:

* GPPsat_mdlpar.csv (contains models parameters)
* GPP_mdlpar.csv

Note: Maybe 2 files with parameters are not necessary some cleaning might be a good idea (initialy the code was spread over 2 files explaining the 2 output files)

# Setup

## Load packages and set paths

```{r ld_pckg, message=FALSE}
# File name : /2013_spavar_LG/report/modelisation/calibration/ER_perCampaign.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade packages (see "Howto" page to install them)
library(bdphdtoolbox)     # personnal toolbox

# CRAN packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)

# Folder to save graphes
savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance"

# Folder to save data treatement
outpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed"

# allow wider tables and graphes in html output
options(width = 100)
knitr::opts_chunk$set(fig.width=12,fig.height=8)

# Load custom color set
source("../../../src/report/custom_colors.R")
# source("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/src/report/custom_colors.R")
```

## Load functions

```{r ld_fn}
pGPP_T <- function(df, x_lab){
par(mar=c(5.1,5.1,2.1,2.1))
plot(Y~X, xlab=x_lab, ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=df)
# curve(a*exp(b*x), add=T, col="blue")
}

# pGPP_Tair <- function(X){
# par(mar=c(5.1,5.1,2.1,2.1))
# plot(GPP~Tair, xlab="température de l'air (°C)",ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# # curve(a*exp(b*x), add=T, col="blue")
# }

pmesmod <- function(df, mdl){
par(mar=c(4,4.5,.5,.5))
plot(Y~predict(mdl), 
     ylim=c(1,14), xlim=c(1,14),
     xlab="", ylab="", data=df)
title(xlab=expression(paste("PBB modélisée (", mu, mol,m^-2,s^-1,")", sep="")), line=2.5)
title(ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
abline(a=0, b=1, col="black", lty=2)
text(19,20, "1:1", srt=45)
}

presmod <- function(mdl){
par(mar=c(4,4,.5,.5))
plot(resid(mdl)~predict(mdl))
title(xlab="valeurs prédites", line=2.5)
title(ylab="résidus", line=2)
}

## Plotting functions
# pmesmod2 <- function(Y, pY){
# par(mar=c(4,4.5,.5,.5))
# plot(Y~pY, 
#      ylim=c(0,15), xlim=c(0,15),
#      xlab="", ylab="", data=df)
# title(xlab=expression(paste("GPP modélisée (", mu, mol,m^-2,s^-1,")", sep="")), line=2.5)
# title(ylab=expression(paste("GPP mesurée (", mu, mol,m^-2,s^-1,")", sep="")), line=2 )
# abline(a=0, b=1, col="black", lty=2)
# text(19,20, "1:1", srt=45)
# }

presmod2 <- function(Y, pY){
par(mar=c(4,4,.5,.5))
plot((Y-pY)~pY,
     xlim=c(0,15),
     xlab="", ylab="")
title(xlab="valeurs prédites", line=2.5)
title(ylab="résidus", line=2)
}


### models fonctions ------------------------------------------------

mdl_june <- function(df, start){
mdl <- nls(Y ~ a * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
}

mdl_linjune <- function(df, start){
mdl <- nls(Y ~ (a*X2 + d) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
}
# mdl_linjune <- function(df, start){
# mdl <- nls(Y ~ (a*X2) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude)
# }

mdl_linlinjune <- function(df, start){
mdl <- nls(Y ~ (a*X2 + d*X3) * exp(-((X-b)/c)^2), data=df, start=start, na.action = na.exclude, trace=T)
}



mdl_param <- function(df, mdl){
  # R2
  devmean <- df$Y-(mean(df$Y)) # deviation à la moyenne
  SSres <-sum((resid(mdl))^2) # Total sum of squares
  SStot <- sum(devmean^2) # Residual sum of squares
  # 2 way to calculate
  # R2 <- (SStot-SSres)/SStot 
  R2 <- 1 - SSres/SStot
  # Adjusted R2
  N <- NROW(devmean) # sample size
  p <- 1 # number of predictors
  R2a <- 1-((1-R2)*(N-1))/(N-p-1)
  # RMSE
  rmse_mdl <- sqrt(mean(((predict(mdl))-df$Y)^2,na.rm=TRUE))
  nrmse_mdl <- 100*rmse_mdl/mean(df$Y)
  # Collect usefull param
  df <- data.frame(a=coef(mdl)[1],
                   b=coef(mdl)[2],
                   c=coef(mdl)[3],
                   d=coef(mdl)[4],
                   a_se=coef(summary(mdl))[,"Std. Error"][1],
                   b_se=coef(summary(mdl))[,"Std. Error"][2],
                   c_se=coef(summary(mdl))[,"Std. Error"][3],
                   d_se=coef(summary(mdl))[,"Std. Error"][4],
                   a_pval=coef(summary(mdl))[,"Pr(>|t|)"][1],
                   b_pval=coef(summary(mdl))[,"Pr(>|t|)"][2],
                   c_pval=coef(summary(mdl))[,"Pr(>|t|)"][3],
                   d_pval=coef(summary(mdl))[,"Pr(>|t|)"][4],
                   R2=R2,
                   aR2=R2a,
                   rmse=rmse_mdl,
                   nrmse=nrmse_mdl,
                   aic=AIC(mdl),
                   bic=BIC(mdl))
  return(df)
}


mdl_indic <- function(Y, pY, mdl){
  mdl <- unique(mdl)
  if(grepl("_", mdl)){
    p <- 2
  }else{ p <- 1}
  # R2
  devmean <- Y-(mean(Y, na.rm=TRUE)) # deviation à la moyenne
  SSres <-sum((Y-pY)^2) # Total sum of squares
  SStot <- sum(devmean^2) # Residual sum of squares
  # 2 way to calculate
  # R2 <- (SStot-SSres)/SStot 
  R2 <- 1 - SSres/SStot
  # Adjusted R2
  N <- NROW(devmean) # sample size
  # p <- 1 # number of predictors
  R2a <- 1-((1-R2)*(N-1))/(N-p-1)
  # RMSE
  rmse_mdl <- sqrt(mean((pY-Y)^2,na.rm=TRUE))
  nrmse_mdl <- 100*rmse_mdl/mean(Y,na.rm=TRUE)
  # Collect usefull param
  df <- data.frame(R2=R2,
                   aR2=R2a,
                   rmse=rmse_mdl,
                   nrmse=nrmse_mdl)
  return(df)
}


get_pGPP <- function(name="Tair", df=df, pred=TRUE){
  temp <- lGPPsatpar %>%
    filter(mdl == name)
  # Vérif nom mdl
  if(NROW(temp) == 0){
    cat("souci avec mdl, pas de paramètres trouvés \n")
  }
  #Savoir si 1 ou plusieur variable création df ER, X1, X2
  if(grepl("_", name)){
    names <- unlist(strsplit(name, "_"))
    dft <- df[,c("GPP", "PAR", names[1], names[2])]
  }else{
    dft <- df[,c("GPP", "PAR", name)]
  }
  # Calcul pER en fonction du nb de par
  if(NCOL(dft) == 3){
    a <- temp$val[1]
    b <- temp$val[2]
    c <- temp$val[3]
    X1 <- dft[,3]
    pGPPsat <- a * exp(-((X1-b)/c)^2)
  }else if(NCOL(dft) == 4){
    a <- temp$val[1]
    b <- temp$val[2]
    c <- temp$val[3]
    d <- temp$val[4]
    X1 <- dft[,3]
    X2 <- dft[,4]
    pGPPsat <- (a*X2 + d) * exp(-((X1-b)/c)^2)
  }else{
    cat("nb de par > 3\n")
  }
  # pGPPsat <- as.vector(pGPPsat[,1])
  # Calcul prediction GPP
#   m <- nls(GPP ~ a*PAR*pGPPsat/(sqrt(pGPPsat^2+(PAR*a)^2)),
#              data=df,
#              start=list(a=-0.05))
  m <- nls(GPP ~ a*PAR*pGPPsat/(pGPPsat+PAR*a),
             data=df,
             start=list(a=0.005))
  i <- coef(m)[1]
  pGPP = (i*dft$PAR*pGPPsat/(sqrt(pGPPsat^2+(dft$PAR*i)^2)))
  # pGPP = (i*dft$PAR*12/(12+dft$PAR*i))
  # pGPP = (i*dft$PAR*pGPPsat/(pGPPsat+dft$PAR*i))
  indic <- data.frame(a=i, AIC=AIC(m), BIC=BIC(m),
                      a_se=coef(summary(m))[,"Std. Error"][1], 
                      a_pval=coef(summary(m))[,"Pr(>|t|)"][1])
  if(pred){
    return(pGPP)
  }else{
    return(indic)
  }
}
```


## Load and transform data

```{r ld_data}
# Load treated data (generated with getClean_fluxesFC)
# Campaign average
df <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC.csv")%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  filter(GPP > 0, PAR > 500) # FILTER to use only PAR saturation measurements 

# Averaging by campaign ---------------------------------------------------
dfm <- df %>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  group_by(ID_camp)%>%
  summarise(
    GPP_sd = sd(GPP, na.rm=T),
    GPP = mean(GPP, na.rm=T),
    ER_sd = sd(ER, na.rm=T),
    ER = mean(ER, na.rm=T),
    NEE_sd = sd(NEE, na.rm=T),
    NEE = mean(NEE, na.rm=T),
    CH4_sd = sd(CH4, na.rm=T),
    CH4 = mean(CH4, na.rm=T),
    date=min(date, na.rm=T),
    timestamp=mean(timestamp, na.rm=T),
    Tair=mean(Tair, na.rm=T),
    TairS=mean(TairS, na.rm=T),
    T5S=mean(T5S, na.rm=T),
    T10S=mean(T10S, na.rm=T),
    T20S=mean(T20S, na.rm=T),
    T40S=mean(T40S, na.rm=T),
    T5=mean(T5, na.rm=T),
    T10=mean(T10, na.rm=T),
    T20=mean(T20, na.rm=T),
    T30=mean(T30, na.rm=T),
    T40=mean(T40, na.rm=T),
    T50=mean(T50, na.rm=T),
    T60=mean(T60, na.rm=T),
    T70=mean(T70, na.rm=T),
    T80=mean(T80, na.rm=T),
    T90=mean(T90, na.rm=T),
    T100=mean(T100, na.rm=T),
    IVcov=mean(IVcov, na.rm=T),
    A=mean(A, na.rm=T),
    H=mean(H, na.rm=T),
    M=mean(M, na.rm=T),
    RH_m=mean(RH_m, na.rm=T),
    NPOC=mean(NPOC, na.rm=T),
    WTL=mean(WTL, na.rm=T)
  )%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))
```

# Calculations
```{r mdl_calc}
# Non linear version --------------------
# Tair june
dmdl_1 <- dfm %>%
  rename(Y=GPP, X=Tair)%>%
  select(Y, X, WTL, RH_m, IVcov, A, H, M)
mdl_1 <- mdl_june(dmdl_1, list(a=20, b=50, c=20))
par_1 <- mdl_param(dmdl_1, mdl_1)

# T5 june
dmdl_2 <- dfm %>%
  rename(Y=GPP, X=T5)%>%
  select(Y, X, WTL, RH_m, IVcov, A, H, M)
mdl_2 <- mdl_june(dmdl_2, list(a=10, b=10, c=10))
par_2 <- mdl_param(dmdl_2, mdl_2)

# Tair + IVcov june
dmdl_1_1 <- dfm %>%
  rename(Y=GPP, X=Tair, X2=IVcov)%>%
  select(Y, X, X2, WTL, RH_m, A, H, M)
mdl_1_1 <- mdl_linjune(dmdl_1_1, list(a=20, b=40, c=20, d=1))
par_1_1 <- mdl_param(dmdl_1_1, mdl_1_1)

# Tair + H june
dmdl_1_2 <- dfm %>%
  rename(Y=GPP, X=Tair, X2=H)%>%
  select(Y, X, X2, WTL, RH_m, IVcov, A, M)
mdl_1_2 <- mdl_linjune(dmdl_1_2, list(a=20, b=40, c=20, d=1))
par_1_2 <- mdl_param(dmdl_1_2, mdl_1_2)

# Tair + A june
dmdl_1_3 <- dfm %>%
  rename(Y=GPP, X=Tair, X2=A)%>%
  select(Y, X, X2, WTL, RH_m, IVcov, H, M)
mdl_1_3 <- mdl_linjune(dmdl_1_3, list(a=20, b=40, c=20, d=1))
par_1_3 <- mdl_param(dmdl_1_3, mdl_1_3)

# T5 + IVcov june
dmdl_2_1 <- dfm %>%
  rename(Y=GPP, X=T5, X2=IVcov)%>%
  select(Y, X, X2, WTL, RH_m, A, H, M)
mdl_2_1 <- mdl_linjune(dmdl_2_1, list(a=10, b=10, c=10, d=1))
par_2_1 <- mdl_param(dmdl_2_1, mdl_2_1)

# T5 + H june
dmdl_2_2 <- dfm %>%
  rename(Y=GPP, X=T5, X2=H)%>%
  select(Y, X, X2, WTL, RH_m, IVcov, A, M)
mdl_2_2 <- mdl_linjune(dmdl_2_2, list(a=10, b=10, c=10, d=1))
par_2_2 <- mdl_param(dmdl_2_2, mdl_2_2)

# dmdl_1_1_1 <- df %>%
#   rename(Y=GPP, X=T5, X2=IVcov, X3=RH_m)%>%
#   select(Y, X, X2, X3, WTL)
# mdl_1_1_1 <- mdl_linlinjune(dmdl_1_1_1, list(a=30, b=50, c=20, d=20))
# par_1_1_1 <- mdl_param(dmdl_1_1_1, mdl_1_1_1)

# dmdl_2_1_1 <- df %>%
#   rename(Y=GPP, X=T5, X2=IVcov, X3=RH_m)%>%
#   select(Y, X, X2, X3, WTL)
# mdl_2_1_1 <- mdl_linlinexp(dmdl_2_1_1)
# par_2_1_1 <- mdl_param(dmdl_2_1_1, mdl_2_1_1)

```

```{r mdl_output}
mdlls <- c("Tair", "T5", "Tair_IVcov", "Tair_H", "Tair_A", "T5_IVcov", "jT5_H")

par <- c(par_1, par_2, par_1_1, par_1_2, par_1_3, par_2_1, par_2_2)
mdlpar <- data.frame(matrix(unlist(par), nrow=length(mdlls), byrow=T))
colnames(mdlpar) <- c("a", "b", "c", "d","a_se", "b_se", "c_se", "d_se", "a_pval", "b_pval", "c_pval", "d_pval", "R2", "R2a", "rmse", "nrmse", "aic", "bic")

res <- data.frame(mdl=mdlls)
res <- cbind(res, mdlpar)

not <- data.frame(best = c("<-","","<-","<-","","",""))

best <- cbind(res, not)%>%
  filter(best == "<-")

result <- res
result[,-1] <- round(result[,-1],2) # round sauf 1re col
result <- cbind(result, not)
```

## Models

```{r}
result
```

## Models sort by R2a

```{r}
result %>%
  select(mdl, R2, R2a, rmse, nrmse, aic, bic, best)%>%
  arrange(desc(R2a))

result %>%
  select(mdl, a, b, c, d, a_se, b_se, c_se, d_se, a_pval, b_pval, c_pval, d_pval)
```

# Diagnostic plots {.tabset}

## GPP~aexp-((Tair-b)/c)

```{r, fig.height=4, eval=T}
par_1
par(mfrow=c(1,3))
pGPP_T(dmdl_1, "température de l'air cm (°C)")
curve(par_1$a*exp(-((x-par_1$b)/par_1$c)^2), add=T, col="blue")
# pmesmod(dmdl_1, mdl_1)
# pmesmod2(dmdl_1$Y, predict(mdl_1))
plt_mesmod(dmdl_1$Y, predict(mdl_1), mes_label = "measured GPP", mod_label = "modelled GPP")
# presmod(mdl_1)
presmod2(dmdl_1$Y, predict(mdl_1))
par(mfrow=c(1,1))

```
```{r, fig.height=7, eval=T}
par(mfrow=c(2,3))
plot(resid(mdl_1)~dmdl_1$WTL, main="vs. WTL") 
plot(resid(mdl_1)~dmdl_1$RH_m, main="vs. RH") 
plot(resid(mdl_1)~dmdl_1$IVcov, main="vs. IV cov")
plot(resid(mdl_1)~dmdl_1$A, main="vs. A")
plot(resid(mdl_1)~dmdl_1$H, main="vs. H")
plot(resid(mdl_1)~dmdl_1$M, main="vs. M")
par(mfrow=c(1,1))
```

## GPP~aexp-((T5-b)/c)

```{r, fig.height=4}
par_2
par(mfrow=c(1,3))
pGPP_T(dmdl_2, "température de la tourbe à -5 cm (°C)")
curve(par_2$a*exp(-((x-par_2$b)/par_2$c)^2), add=T, col="blue")
# pmesmod(dmdl_2, mdl_2)
plt_mesmod(dmdl_2$Y, predict(mdl_2), mes_label = "measured GPP", mod_label = "modelled GPP")
presmod(mdl_2)
par(mfrow=c(1,1))

# par(mfrow=c(1,3))
# plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_2$RH_m, main="vs. RH") 
# plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
# par(mfrow=c(1,1))
```
```{r, fig.height=7}
par(mfrow=c(2,3))
plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
plot(resid(mdl_2)~dmdl_2$RH_m, main="vs. RH") 
plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
plot(resid(mdl_2)~dmdl_2$A, main="vs. A")
plot(resid(mdl_2)~dmdl_2$H, main="vs. H")
plot(resid(mdl_2)~dmdl_2$M, main="vs. M")
par(mfrow=c(1,1))
```


## GPP~(a*H) * exp-((Tair-b)/c)

```{r, fig.height=4, eval=FALSE}
par_1_2
par(mfrow=c(1,3))
pGPP_T(dmdl_1_2, "température de l'air (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
# pmesmod(dmdl_1_2, mdl_1_2)
plt_mesmod(dmdl_1_2$Y, predict(mdl_1_2), mes_label = "measured GPP", mod_label = "modelled GPP")
presmod(mdl_1_2)
par(mfrow=c(1,1))

```

## GPP~(a*IVcov) * exp-((Tair-b)/c)

```{r, fig.height=4, eval=T}
par_1_1
par(mfrow=c(1,3))
pGPP_T(dmdl_1_1, "température de l'air (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
# pmesmod(dmdl_1_1, mdl_1_1)
plt_mesmod(dmdl_1_1$Y, predict(mdl_1_1), mes_label = "measured GPP", mod_label = "modelled GPP")
presmod(mdl_1_1)
par(mfrow=c(1,1))

# par(mfrow=c(1,3))
# plot(resid(mdl_2)~dmdl_2$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_2$RH_m, main="vs. RH") 
# plot(resid(mdl_2)~dmdl_2$IVcov, main="vs. IV cov")
# par(mfrow=c(1,1))
```

## GPP~(a*H) * exp-((T5-b)/c)

```{r, fig.height=4, eval=FALSE}
par_2_2
par(mfrow=c(1,3))
pGPP_T(dmdl_2_2, "température de la tourbe à -5 cm (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
# pmesmod(dmdl_2_2, mdl_2_2)
plt_mesmod(dmdl_2_2$Y, predict(mdl_2_2), mes_label = "measured GPP", mod_label = "modelled GPP")
presmod(mdl_2_2)
par(mfrow=c(1,1))
```

## GPP~(a*IVcov) * exp-((T5-b)/c)

```{r, fig.height=4}
par_2_1
par(mfrow=c(1,3))
pGPP_T(dmdl_2_1, "température de la tourbe à -5 cm (°C)")
# curve(par_1_1$a*exp(-((x-par_1_1$b)/par_1_1$c)^2), add=T, col="blue")
# pmesmod(dmdl_2_1, mdl_2_1)
plt_mesmod(dmdl_2_1$Y, predict(mdl_2_1), mes_label = "measured GPP", mod_label = "modelled GPP")
presmod(mdl_2_1)
par(mfrow=c(1,1))
```

# Figures

```{r, fig.height=8}
labpar_1 <- format(par_1,  digits=2, nsmall=2)
labpar_1_1 <- format(par_1_1,  digits=2, nsmall=2)
labpar_2 <- format(par_2,  digits=2, nsmall=2)
labpar_1_2 <- format(par_1_2,  digits=2, nsmall=2)
labpar_2_1 <- format(par_2_1,  digits=2, nsmall=2)
# labpar_2_3 <- format(par_2_3,  digits=2, nsmall=2)


lab11 <- paste(
  "y = ", labpar_1$a, " * exp(", labpar_1$b, "*Tair)",
  "\nR² = ", labpar_1$aR2, 
  "\nRMSE = ", labpar_1$rmse,
  "\nNRMSE = ", labpar_1$nrmse, " %", sep="")
lab11_1 <- paste(
  "y = ", labpar_1_1$a, " * IV + ", labpar_1_1$c ,"exp(", labpar_1_1$b, "*Tair)",
  "\nR² = ", labpar_1_1$aR2, 
  "\nRMSE = ", labpar_1_1$rmse,
  "\nNRMSE = ", labpar_1_1$nrmse, " %", sep="")
lab21 <- paste0(
  "y = ", labpar_2$a, " * exp(", labpar_2$b, "*T5)",
  "\nR² = ", labpar_2$aR2, 
  "\nRMSE = ", labpar_2$rmse,
  "\nNRMSE = ", labpar_2$nrmse, " %", sep="")
lab21_1 <- paste(
  "y = ", labpar_2_1$a, " * IV + ", labpar_2_1$c ,"exp(", labpar_2_1$b, "*Tair)",
  "\nR² = ", labpar_2_1$aR2, 
  "\nRMSE = ", labpar_2_1$rmse,
  "\nNRMSE = ", labpar_2_1$nrmse, " %", sep="")

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_T5_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
# pmesmod(dmdl_2, mdl_2)
plt_mesmod(dmdl_2$Y, predict(mdl_2), mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=.4, y=12, labels=lab21, adj=0)
plot(resid(mdl_2)~predict(mdl_2), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_T5IV_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
# pmesmod(dmdl_2_1, mdl_2_1)
plt_mesmod(dmdl_2_1$Y, predict(mdl_2_1), mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=.4, y=12, labels=lab21_1, adj=0)
plot(resid(mdl_2_1)~predict(mdl_2_1), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))
# 
cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_T5_mdl_res.pdf"), width=5, height=4)
par(mfrow=c(1,1), mar=c(4,4.5,.5,.5))
# plot(resid(mdl_2)~dmdl_1$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_1$RH, main="vs. RH") 
plot(resid(mdl_2)~dmdl_2$IVcov,
     xlab="indice de végétation",
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep=""))) 
par(mfrow=c(1,1))

##################### Tair


cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_Tair_mesmod.pdf"), width=9, height=8)
par(mfrow=c(2,2))
## haut gauche
# pmesmod(dmdl_1, mdl_1)
plt_mesmod(dmdl_1$Y, predict(mdl_1), mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=1, y=12.5, labels=lab11, adj=0)
text(x=13, y=2, labels="a", adj=0, cex=2)

## haut droite
plot(resid(mdl_1)~predict(mdl_1), xlab="", ylab="")
title(xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")), line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=13, y=-4, labels="b", adj=0, cex=2)

## bas gauche
plot(resid(mdl_1)~dmdl_1$IVcov, xlab="", ylab="") 
title(xlab="indice de végétation", line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=.5, y=-4, labels="c", adj=0, cex=2)

## bas droite
plot(resid(mdl_1)~dmdl_1$WTL, xlab="", ylab="") 
title(xlab="Niveau de la nappe (cm)", line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=17, y=-4, labels="d", adj=0, cex=2)

par(mfrow=c(1,1))

##################$ TairIVcov

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_TairIV_mesmod.pdf"), width=9, height=4)
par(mfrow=c(1,2))
## haut gauche
# pmesmod(dmdl_1_1, mdl_1_1)
plt_mesmod(dmdl_1_1$Y, predict(mdl_1_1), mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=1, y=12.5, labels=lab11_1, adj=0)
text(x=13, y=2, labels="a", adj=0, cex=2)

## haut droite
plot(resid(mdl_1_1)~predict(mdl_1_1), xlab="", ylab="")
title(xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")), line=2.5)
title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
text(x=12.3, y=-1.65, labels="b", adj=0, cex=2)

## bas gauche
# plot(resid(mdl_1_1)~dmdl_1_1$IVcov, xlab="", ylab="") 
# title(xlab="indice de végétation", line=2.5)
# title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
# text(x=.5, y=-4, labels="c", adj=0, cex=2)
# 
# ## bas droite
# plot(resid(mdl_1_1)~dmdl_1_1$WTL, xlab="", ylab="") 
# title(xlab="Niveau de la nappe (cm)", line=2.5)
# title(ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")), line=2)
# text(x=17, y=-4, labels="d", adj=0, cex=2)

par(mfrow=c(1,1))




cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_Tair_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
# pmesmod(dmdl_1, mdl_1)
plt_mesmod(dmdl_1$Y, predict(mdl_1), mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=.4, y=12, labels=lab11, adj=0)
plot(resid(mdl_1)~predict(mdl_1), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_TairIV_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
# pmesmod(dmdl_1_1, mdl_1_1)
plt_mesmod(dmdl_1_1$Y, predict(mdl_1_1), mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=.4, y=12, labels=lab11_1, adj=0)
plot(resid(mdl_1_1)~predict(mdl_1_1), 
     xlab=expression(paste("Valeurs prédites (", mu, mol,m^-2,s^-1,")", sep="")),
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep="")))
par(mfrow=c(1,1))
# 
cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPPsat_Tair_mdl_res.pdf"), width=5, height=4)
par(mfrow=c(1,1), mar=c(4,4.5,.5,.5))
# plot(resid(mdl_2)~dmdl_1$WTL, main="vs. WTL") 
# plot(resid(mdl_2)~dmdl_1$RH, main="vs. RH") 
plot(resid(mdl_1)~dmdl_1$IVcov,
     xlab="indice de végétation",
     ylab=expression(paste("Résidus (", mu, mol,m^-2,s^-1,")", sep=""))) 
par(mfrow=c(1,1))
# 
# 
# cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance", "PPB_1par_mdl_res.pdf"), width=10, height=8)
# par(mfrow=c(2,2))
# pmesmod(dmdl_1, mdl_1)
# text(x=1, y=8, labels=lab11, adj=0)
# plot(resid(mdl_1)~dmdl_1$H, main="vs. H") 
# pmesmod(dmdl_2, mdl_2)
# text(x=1, y=8, labels=lab21, adj=0)
# plot(resid(mdl_2)~dmdl_1$RH_m, main="vs. TES") 
# par(mfrow=c(1,1))
# 
# lab11 <- paste(
#   "y = (", labpar_1_2$a, " * H + ", labpar_1_2$c, ") * exp(", labpar_1_2$b, "*Tair)",
#   "\nR² = ", labpar_1_2$aR2, 
#   "\nNRMSE = ", labpar_1_2$nrmse, sep="")
# # lab21 <- paste0(
# #   "y = (", labpar_2_3$a, " * TES + ", labpar_2_3$c, ") * exp(", labpar_2_3$b, "*T5)",
# #   "\nR² = ", labpar_2_3$aR2, 
# #   "\nNRMSE = ", labpar_2_3$nrmse)
# # 
# cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance", "PPB_2par_mdl.pdf"), width=5, height=4)
# par(mfrow=c(1,1))
# pmesmod(dmdl_1_2, mdl_1_2)
# text(x=1, y=8, labels=lab11, adj=0)
# # plot(resid(mdl_1)~dmdl_1$H, main="vs. H") 
# # pmesmod(dmdl_2_3, mdl_2_3)
# # text(x=1, y=18, labels=lab21, adj=0)
# # # plot(resid(mdl_2)~dmdl_1$RH_m, main="vs. TES") 
# par(mfrow=c(1,1))

```

# Data
```{r sav_mdl_par}
select(best, -best)

export <- res %>%
  select(mdl, a, b, c, d)

write.csv(export, file.path(outpth, "GPPsat_mdlpar.csv"), quote=F, row.names=F)
```

# Non sat

TODO put cb_GPP_avg_2.Rmd there
```{r}
lGPPsatpar <- export %>%
  gather(par, value, 2:5)%>%
  do(na.omit(.))%>%
  arrange(mdl, par)
```

```{r}
# /!\ 2 versions /!\
# VERSION 1 : Données moyennées sans retrait des NA au préalable
# Load treated data (generated with getClean_fluxesFC)
# Campaign average
# dfm <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC_avg.csv")%>%
#   mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
#   mutate(date=as.POSIXct(as.character(date)))%>%
#   select(date, GPP, PAR, Tair, T5, IVcov, H, RH_m)

# VERSION 2 (thèse) : Données moyennées après retrait des NA
df <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC.csv")%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))%>%
  select(placette, date, ID_camp, ER, GPP, NEE, Tair, T5, WTL, PAR, RH_m, H, IVcov, IVcov_area)%>%
  do(na.omit(.)) # Ligne qui fait la différence entre les deux versions

dfm <- df %>%
  group_by(ID_camp)%>%
  summarise(date=min(date, na.rm=T),
            GPP=mean(GPP, na.rm=T),
            Tair=mean(Tair, na.rm=T),
            T5=mean(T5, na.rm=T),
            PAR=mean(PAR, na.rm=T),
            WTL=mean(WTL, na.rm=T),
            RH=mean(RH_m, na.rm=T),
            H=mean(H, na.rm=T),
            IVcov=mean(IVcov, na.rm=T),
            IVcov_area=mean(IVcov_area, na.rm=T)
            )
dfm <- as.data.frame(dfm)

# /!\ 2 versions /!\
# Résultats légèrement différent de ceux de la thèse car pour cette dernière j'avais enlevé toutes les lignes contenant des NA sur les variables qui m'intéressait avant de faire les moyennes (do(na.omit(.)))...
```

```{r}
# Liste des modèles à tester
GPP_par <- c("Tair", "T5", "Tair_H", "Tair_IVcov", "T5_IVcov")

# Calcul prediction NEE
GPPpred <- data.frame()
GPPpar <- data.frame()
for (i in GPP_par){
    # mdl pred
    pGPP <- get_pGPP(i, dfm, pred = T) # get prediction
    temp <- data.frame(GPP=dfm$GPP, mdl=i, pGPP=pGPP)
    GPPpred <- rbind(GPPpred,temp)
    # mdl par
    par <- get_pGPP(i, dfm, pred = F) # get model param
    tmp <- cbind(mdl=i, par)
    # tmp <- data.frame(mdl=i, a=par)
    GPPpar <- rbind(GPPpar, tmp)
}

# Export paramètre mdl GPP
write.csv(GPPpar[,1:2], file.path(outpth, "GPP_mdlpar.csv"), quote=F, row.names=F)
```

# Results GPP {.tabset}

```{r}
GPPind <- GPPpar
# Tableau resultats modèles
ldf <- GPPpred %>%
  group_by(mdl)%>%
  do(mdl_indic(.$GPP, .$pGPP, mdl=.$mdl))%>%
  ungroup()%>%
  inner_join(., GPPind)%>%
  arrange(desc(aR2))

ldf[,2:10] <- round(ldf[,2:10], 2)
ldf
```

## Tair

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "Tair")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
presmod2(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
```

## Tair + IVcov

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "Tair_IVcov")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
presmod2(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
```

## T5

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "T5")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
presmod2(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
iT5 <- mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
iT5
```

## T5 + IVcov

```{r, fig.width=8, fig.height=4}
dat <- filter(GPPpred, mdl == "T5_IVcov")
par(mfrow=c(1,2))
plt_mesmod(dat$GPP, dat$pGPP, mes_label = "measured GPP", mod_label = "modelled GPP")
presmod2(dat$GPP, dat$pGPP)
par(mfrow=c(1,1))
iT5_IV <- mdl_indic(dat$GPP, dat$pGPP, mdl=dat$mdl)
iT5_IV
```


# Figures

```{r, fig.height=8, result="hide"}
dat_Ta <- filter(GPPpred, mdl == "Tair")
labf <- format(mdl_indic(dat_Ta$GPP, dat_Ta$pGPP, mdl=dat_Ta$mdl), digits=2, nsmall=2)
lab_Ta <- paste0(
  "y = ", labf$a, " * exp(", labf$b, "*T5)",
  "\nR² = ", labf$aR2, 
  "\nRMSE = ", labf$rmse,
  "\nNRMSE = ", labf$nrmse, " %", sep="")

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPP_Tair_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))
plt_mesmod(dat_Ta$GPP, dat_Ta$pGPP, mes_label = "PPB mesurée", mod_label = "PPB modélisée")
# pmesmod2(dat_Ta$GPP, dat_Ta$pGPP)
text(x=.4, y=12, labels=lab_Ta, adj=0)
presmod2(dat_Ta$GPP, dat_Ta$pGPP)
par(mfrow=c(1,1))
```

```{r}
dat_TaIV <- filter(GPPpred, mdl == "Tair_IVcov")
labf <- format(mdl_indic(dat_TaIV$GPP, dat_TaIV$pGPP, mdl=dat_TaIV$mdl), digits=2, nsmall=2)
lab_TaIV <- paste0(
  "y = ", labf$a, " * exp(", labf$b, "*T5)",
  "\nR² = ", labf$aR2, 
  "\nRMSE = ", labf$rmse,
  "\nNRMSE = ", labf$nrmse, " %", sep="")

cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPP_TairIV_mdl_mesmod.pdf"), width=10, height=4)
par(mfrow=c(1,2))

# pmesmod2(dat_TaIV$GPP, dat_TaIV$pGPP)
plt_mesmod(dat_TaIV$GPP, dat_TaIV$pGPP, mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=.4, y=12, labels=lab_TaIV, adj=0)
presmod2(dat_TaIV$GPP, dat_TaIV$pGPP)
par(mfrow=c(1,1))
```

```{r}
# Fig Tair res + Tair IV res
cairo_pdf(file.path("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPP", "GPP_mdl_mesmod_sig.pdf"), width=9, height=8)
par(mfrow=c(2,2))

# Haut
# pmesmod2(dat_Ta$GPP, dat_Ta$pGPP)
plt_mesmod(dat_Ta$GPP, dat_Ta$pGPP, mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=.4, y=13, labels=lab_Ta, adj=0)
text(x=14, y=1, labels="a", adj=0, cex=2)
presmod2(dat_Ta$GPP, dat_Ta$pGPP)
text(x=14, y=-3.7, labels="b", adj=0, cex=2)
# Bas
# pmesmod2(dat_TaIV$GPP, dat_TaIV$pGPP)
plt_mesmod(dat_TaIV$GPP, dat_TaIV$pGPP, mes_label = "PPB mesurée", mod_label = "PPB modélisée")
text(x=.4, y=13, labels=lab_TaIV, adj=0)
text(x=14, y=1, labels="c", adj=0, cex=2)
presmod2(dat_TaIV$GPP, dat_TaIV$pGPP)
text(x=14, y=-1.6, labels="d", adj=0, cex=2)

par(mfrow=c(1,1))
```


