---
title: "global ER model per year"
author: "Benoît D'ANGELO"
date: "07/04/2015"
output:
  html_document:
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
---

<h3><a href="../CB_toc.html"> Carbon balance </a></h3>

***

```{r setup, echo=FALSE, message=FALSE}
rm(list=ls(all=TRUE))

library(laguettevarspa)
library(snoweather)
library(bdphdtoolbox)

# library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)

savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance"

knitr::opts_chunk$set(fig.width=12,fig.height=8,echo=FALSE, warning=FALSE,message=FALSE)
options(width = 100)
```


```{r load data}
# Fichier VS -- Données ponctuelles
# préparation donnée vég
dfveg <- svVegetation %>%
  group_by(ID_camp, placette)%>%
  filter(specie == "molinia")%>%
  mutate(area_m = mol_LtoS(height_m*10),
         area = area_m * number)%>%
  select(ID_camp, placette, number, area)
  
dfveg$area <- ifelse(dfveg$number == 0, 0, dfveg$area)
# Fichier VS -- Données ponctuelles
df <- svNetFlux %>%
  filter(type == "ER")%>%
  select(timestamp, ID_camp, placette, R2, pvalue, mtime, netCO2F)%>%
  left_join(., svTemperature, by=c("ID_camp", "placette")) %>%
  left_join(., svCtrlFact, by=c("ID_camp", "placette")) %>%
  left_join(., dfveg, by=c("ID_camp", "placette"))%>%
  select(ID_camp,date.x, placette, R2, pvalue, mtime, netCO2F, T10, T15, T20, T25, WTL, RH_m, area)%>%
  separate(date.x, c("year", "m", "d"))%>%
  filter(netCO2F > 0) # remove value below 0
  # mutate(T25_borto = (T25+5)/(15+5))
```


```{r functions}
pER_T <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~T25, xlab="température à -25 cm (°C)",ylab=expression(paste("Re mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# curve(a*exp(b*x), add=T, col="blue")
}

pmesmod <- function(X, ttl){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~predman, ylim=c(0,20), xlim=c(0,20),xlab=expression(paste("Re modélisée (", mu, mol,m^-2,s^-1,")", sep=""))
, ylab=expression(paste("Re mesurée (", mu, mol,m^-2,s^-1,")", sep="")), main=ttl, data=X)
abline(a=0, b=1, col="black", lty=2)
text(19,20, "1:1", srt=45)
}

```


# ER representation

According to <a href="../../relation_flux_T/ER_T.html"> this document </a> the best ER representation with temperature at global scale is found by using an exponential model with -25 cm depth temperature.

# Temperature, ER~aexp(bT25)

```{r calc mdl}
# Linear version ------------------------
# df_mT2013_lm <- df%>%
#   filter(year == "2013")
# 
# mT2013_lm <- lm(log(netCO2F)~T25, data = df_mT2013_lm, na.action = na.exclude)
# 
# a <- exp(coef(mT2013_lm)[1])
# b <- coef(mT2013_lm)[2]
# 
# df_mT2013_lm$resi <- residuals(mT2013_lm)
# df_mT2013_lm$pred <- predict(mT2013_lm)
# df_mT2013_lm$predman <- a*exp(b*df_mT2013_lm$T25)
# 
# rmse_ER_T25_lm <- sqrt(mean((df_mT2013_lm$predman-df_mT2013_lm$netCO2F)^2,na.rm=TRUE))

# Non linear version --------------------
## 2013 
df_mT2013 <- df%>%
  filter(year == "2013")

mT2013 <- nls(netCO2F~a*exp(b*T25), data = df_mT2013, na.action = na.exclude, start=list(a=0.2, b=0.2))

a2013 <- coef(mT2013)[1]
b2013 <- coef(mT2013)[2]

df_mT2013$resi <- residuals(mT2013)
df_mT2013$pred <- predict(mT2013)
df_mT2013$predman <- a2013*exp(b2013*df_mT2013$T25)

rmse_ER_T25_2013 <- sqrt(mean((df_mT2013$predman-df_mT2013$netCO2F)^2,na.rm=TRUE))
## 2014 
df_mT2014 <- df%>%
  filter(year == "2014")

mT2014 <- nls(netCO2F~a*exp(b*T25), data = df_mT2014, na.action = na.exclude, start=list(a=0.2, b=0.2))

a2014 <- coef(mT2014)[1]
b2014 <- coef(mT2014)[2]

df_mT2014$resi <- residuals(mT2014)
df_mT2014$pred <- predict(mT2014)
df_mT2014$predman <- a2014*exp(b2014*df_mT2014$T25)

rmse_ER_T25_2014 <- sqrt(mean((df_mT2014$predman-df_mT2014$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=12}
par(mfrow=c(2,2))
pER_T(df_mT2013)
curve(a2013*exp(b2013*x), add=T, col="blue")
pER_T(df_mT2014)
curve(a2014*exp(b2014*x), add=T, col="blue")
pmesmod(df_mT2013, "2013")
pmesmod(df_mT2014, "2014")
par(mfrow=c(2,1))
```

### model equation

#### 2013
ER = `r a2013` * exp(`r b2013` * T25)

#### 2014
ER = `r a2014` * exp(`r b2014` * T25)

### diagnostic values

#### 2013

rmse = `r rmse_ER_T25_2013` (nls)

aic = `r AIC(mT2013)` (nls)

#### 2014
rmse = `r rmse_ER_T25_2014` (nls)

aic = `r AIC(mT2014)` (nls)



```{r exprt_fig, error=FALSE, results="hide"}
#2013
cairo_pdf(file.path(savpth, "ER_T25_ecosyt_2013.pdf"), width=6.5, height=5)
pER_T(df_mT2013)
curve(a2013*exp(b2013*x), add=T, col="blue")
dev.off()
#2014
cairo_pdf(file.path(savpth, "ER_T25_ecosyt_2014.pdf"), width=6.5, height=5)
pER_T(df_mT2014)
curve(a2014*exp(b2014*x), add=T, col="blue")
dev.off()

# Mesurée vs modélisée ------------------
#2013
cairo_pdf(file.path(savpth, "ER_T25_ecosyt_mesmod_2013.pdf"), width=5, height=5)
pmesmod(df_mT2013, "2013")
dev.off()
#2013
cairo_pdf(file.path(savpth, "ER_T25_ecosyt_mesmod_2014.pdf"), width=5, height=5)
pmesmod(df_mT2014, "2014")
dev.off()
```



## Residual vs other controlling factors

### 2013
```{r, fig.height=6}
par(mfrow=c(1,3))
plot(df_mT2013$resi~df_mT2013$WTL, main="vs. WTL") 
plot(df_mT2013$resi~df_mT2013$RH_m, main="vs. RH") 
# plot(df_mT2013$resi~df_mT2013$area, main="vs. pseudoLAI") 
par(mfrow=c(1,1))
```

### 2014
```{r, fig.height=6}
par(mfrow=c(1,3))
plot(df_mT2014$resi~df_mT2014$WTL, main="vs. WTL") 
plot(df_mT2014$resi~df_mT2014$RH_m, main="vs. RH") 
plot(df_mT2014$resi~df_mT2014$area, main="vs. pseudoLAI", xlim=c(0, 300000)) 
par(mfrow=c(1,1))
```



















# Temperature and Relative humidity ER~(aRH+b)*exp(cT25)
```{r}
# Non linear version --------------------
# 2013
df_mrh2013 <- df%>%
  filter(year == "2013")

mrh2013 <- nls(netCO2F~(a*RH_m + b)*exp(c*T25), data = df_mrh2013, na.action = na.exclude, start=list(a=0.2, b=0.2, c=0.6))

a2013 <- coef(mrh2013)[1]
b2013 <- coef(mrh2013)[2]
c2013 <- coef(mrh2013)[3]

df_mrh2013$resi <- residuals(mrh2013)
df_mrh2013$pred <- predict(mrh2013)
df_mrh2013$predman <- (a2013*df_mrh2013$RH_m + b2013)*exp(c2013*df_mrh2013$T25)

rmse_ER_RHT25_2013 <- sqrt(mean((df_mrh2013$predman-df_mrh2013$netCO2F)^2,na.rm=TRUE))

# 2014
df_mrh2014 <- df%>%
  filter(year == "2014")

mrh2014 <- nls(netCO2F~(a*RH_m + b)*exp(c*T25), data = df_mrh2014, na.action = na.exclude, start=list(a=0.2, b=0.2, c=0.6))

a2014 <- coef(mrh2014)[1]
b2014 <- coef(mrh2014)[2]
c2014 <- coef(mrh2014)[3]

df_mrh2014$resi <- residuals(mrh2014)
df_mrh2014$pred <- predict(mrh2014)
df_mrh2014$predman <- (a2014*df_mrh2014$RH_m + b2014)*exp(c2014*df_mrh2014$T25)

rmse_ER_RHT25_2014 <- sqrt(mean((df_mrh2014$predman-df_mrh2014$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=12}
par(mfrow=c(2,2))
pER_T(df_mrh2013)
pER_T(df_mrh2014)
pmesmod(df_mrh2013, "2013")
pmesmod(df_mrh2014, "2014")
par(mfrow=c(2,1))
```

### model equation

#### 2013
ER = (`r a2013` * RH + `r b2013`) * exp(`r c2013` * T25)

#### 2014
ER = (`r a2014` * RH + `r b2014`) * exp(`r c2014` * T25)

### diagnostic values

#### 2013
rmse = `r rmse_ER_RHT25_2013` (nls)

aic = `r AIC(mrh2013)` (nls)

#### 2014
rmse = `r rmse_ER_RHT25_2014` (nls)

aic = `r AIC(mrh2014)` (nls)

```{r, error=FALSE, results="hide"}
# 2013
cairo_pdf(file.path(savpth, "ER_RHT25_ecosyt_2013.pdf"), width=6.5, height=5)
pER_T(df_mrh2013)
dev.off()

cairo_pdf(file.path(savpth, "ER_RHT25_ecosyt_mesmod_2013.pdf"), width=5, height=5)
pmesmod(df_mrh2013, "2013")
dev.off()

# 2014
cairo_pdf(file.path(savpth, "ER_RHT25_ecosyt_2014.pdf"), width=6.5, height=5)
pER_T(df_mrh2014)
dev.off()

cairo_pdf(file.path(savpth, "ER_RHT25_ecosyt_mesmod_2014.pdf"), width=5, height=5)
pmesmod(df_mrh2014, "2014")
dev.off()
```










# Temperature, Relative humidity, pseudo LAI, ER~(aRH+(bLAI))*exp(cT25)

Pas de données mesurées en 2013 pour le nombre de molinie

```{r}
# Non linear version --------------------
# 2013
# Pas données

# 2014
df_mrhveg2014 <- df%>%
  filter(year == "2014")

mrhveg2014 <- nls(netCO2F~(a*RH_m + (b*area))*exp(c*T25), data = df_mrhveg2014, na.action = na.exclude, start=list(a=0.2, b=0.2, c=0.6))

a2014 <- coef(mrhveg2014)[1]
b2014 <- coef(mrhveg2014)[2]
c2014 <- coef(mrhveg2014)[3]

df_mrhveg2014$resi <- residuals(mrhveg2014)
df_mrhveg2014$pred <- predict(mrhveg2014)
df_mrhveg2014$predman <- (a2014*df_mrhveg2014$RH_m + (b2014*df_mrhveg2014$area))*exp(c2014*df_mrhveg2014$T25)

rmse_ER_RHvegT25_2014 <- sqrt(mean((df_mrhveg2014$predman-df_mrhveg2014$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=6}
par(mfrow=c(1,2))
# pER_T(df_mrhveg2013)
pER_T(df_mrhveg2014)
# pmesmod(df_mrhveg2013, "2013")
pmesmod(df_mrhveg2014, "2014")
par(mfrow=c(1,1))
```

### model equation

#### 2014
ER = (`r a2014` * RH + `r b2014`) * exp(`r c2014` * T25)

### diagnostic values

#### 2014
rmse = `r rmse_ER_RHvegT25_2014` (nls)

aic = `r AIC(mrhveg2014)` (nls)

```{r, error=FALSE, results="hide"}
# 2013
# 2014
cairo_pdf(file.path(savpth, "ER_RHvegT25_ecosyt_2014.pdf"), width=6.5, height=5)
pER_T(df_mrhveg2014)
dev.off()

cairo_pdf(file.path(savpth, "ER_RHvegT25_ecosyt_mesmod_2014.pdf"), width=5, height=5)
pmesmod(df_mrhveg2014, "2014")
dev.off()
```

