---
title: "global ER model"
author: "Benoît D'ANGELO"
date: "07/04/2015"
output:
  html_document:
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
---

<h3><a href="../CB_toc.html"> Carbon balance </a></h3>

***

```{r setup, echo=FALSE, message=FALSE}
rm(list=ls(all=TRUE))

library(laguettevarspa)
library(snoweather)
library(bdphdtoolbox)

# library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)

savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance"

knitr::opts_chunk$set(fig.width=12,fig.height=8,echo=FALSE, warning=FALSE,message=FALSE)
options(width = 100)
```


```{r load data}
# Fichier VS -- Données ponctuelles
# préparation donnée vég
dfveg <- svVegetation %>%
  group_by(ID_camp, placette)%>%
  filter(specie == "molinia")%>%
  mutate(area_m = mol_LtoS(height_m*10),
         area = area_m * number)%>%
  select(ID_camp, placette, number, area)
dfveg$area <- ifelse(dfveg$number == 0, 0, dfveg$area)

# Fichier VS -- Données ponctuelles
df <- svNetFlux %>%
  filter(type == "ER")%>%
  select(timestamp, ID_camp, placette, R2, pvalue, mtime, netCO2F)%>%
  left_join(., svTemperature, by=c("ID_camp", "placette")) %>%
  left_join(., svCtrlFact, by=c("ID_camp", "placette")) %>%
  left_join(., dfveg, by=c("ID_camp", "placette"))%>%
  select(ID_camp, placette, R2, pvalue, mtime, netCO2F, T10, T15, T20, T25, WTL, RH_m, area)%>%
  filter(netCO2F > 0) # remove value below 0
  # mutate(T25_borto = (T25+5)/(15+5))
```


```{r functions}
pER_T <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~T25, xlab="température à -25 cm (°C)",ylab=expression(paste("Re mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# curve(a*exp(b*x), add=T, col="blue")
}

pmesmod <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~predman, ylim=c(0,20), xlim=c(0,20),xlab=expression(paste("Re modélisée (", mu, mol,m^-2,s^-1,")", sep=""))
, ylab=expression(paste("Re mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
abline(a=0, b=1, col="black", lty=2)
text(19,20, "1:1", srt=45)
}

```


# ER representation

According to <a href="../../relation_flux_T/ER_T.html"> this document </a> the best ER representation with temperature at global scale is found by using an exponential model with -25 cm depth temperature.

# Temperature, ER~aexp(bT25)

```{r calc mdl}
# Linear version ------------------------
df_mT_lm <- df

mT_lm <- lm(log(netCO2F)~T25, data = df_mT_lm, na.action = na.exclude)

a <- exp(coef(mT_lm)[1])
b <- coef(mT_lm)[2]

df_mT_lm$resi <- residuals(mT_lm)
df_mT_lm$pred <- predict(mT_lm)
df_mT_lm$predman <- a*exp(b*df_mT_lm$T25)

rmse_ER_T25_lm <- sqrt(mean((df_mT_lm$predman-df_mT_lm$netCO2F)^2,na.rm=TRUE))

# Non linear version --------------------
df_mT <- df

mT <- nls(netCO2F~a*exp(b*T25), data = df_mT, na.action = na.exclude, start=list(a=0.2, b=0.2))

a <- coef(mT)[1]
b <- coef(mT)[2]

df_mT$resi <- residuals(mT)
df_mT$pred <- predict(mT)
df_mT$predman <- a*exp(b*df_mT$T25)

rmse_ER_T25 <- sqrt(mean((df_mT$predman-df_mT$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=6}
par(mfrow=c(1,2))
pER_T(df_mT)
curve(a*exp(b*x), add=T, col="blue")
pmesmod(df_mT)
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * exp(`r b` * T25)

### diagnostic values

rmse = `r rmse_ER_T25` (nls)

aic = `r AIC(mT)` (nls)

***

rmse = `r rmse_ER_T25_lm` (lm)

aic = `r AIC(mT_lm)` (lm)

```{r exprt_fig, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "ER_T25_ecosyt.pdf"), width=6.5, height=5)
pER_T(df_mT)
curve(a*exp(b*x), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "ER_T25_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mT)
dev.off()
```




## Residual vs other controlling factors

```{r, fig.height=9}
par(mfrow=c(2,2))
plot(df_mT$resi~df_mT$WTL, main="vs. WTL") 
plot(df_mT$resi~df_mT$RH_m, main="vs. RH") 
plot(df_mT$resi~df_mT$area, main="vs. pseudoLAI") 

par(mfrow=c(1,1))
```

# Temperature and Relative humidity ER~(aRH+b)*exp(cT25)
```{r}
# Non linear version --------------------
df_mrh <- df

mrh <- nls(netCO2F~(a*RH_m + b)*exp(c*T25), data = df_mrh, na.action = na.exclude, start=list(a=0.2, b=0.2, c=0.6))

a <- coef(mrh)[1]
b <- coef(mrh)[2]
c <- coef(mrh)[3]

df_mrh$resi <- residuals(mrh)
df_mrh$pred <- predict(mrh)
df_mrh$predman <- (a*df_mrh$RH_m + b)*exp(c*df_mrh$T25)

rmse_ER_RHT25 <- sqrt(mean((df_mrh$predman-df$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=6}
par(mfrow=c(1,2))
pER_T(df_mrh)
pmesmod(df_mrh)
par(mfrow=c(1,1))
```

### model equation

ER = (`r a` * RH + `r b`) * exp(`r c` * T25)

### diagnostic values

rmse = `r rmse_ER_RHT25` (nls)

aic = `r AIC(mrh)` (nls)

```{r, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "ER_RHT25_ecosyt.pdf"), width=6.5, height=5)
pER_T(df_mrh)
dev.off()

cairo_pdf(file.path(savpth, "ER_RHT25_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mrh)
dev.off()
```


***
***
***

# Diagnostic plot

## ER~T25 all data points (nls)

### model summary
```{r}
summary(mT)
# lm_get_exp(mT_lm, details = "all")
```

### Check for normality of the residuals
```{r}
par(mfrow=c(1,2))
hist(df_mT$resi)
qqnorm(df_mT$resi)
qqline(df_mT$resi)
par(mfrow=c(1,1))

plot(df_mT$resi~df_mT$predman)

```

## ER~T25 all data points (lm)

### model summary
```{r}
summary(mT_lm)
lm_get_exp(mT_lm, details = "all")
```

### Check for normality of the residuals

```{r, fig.height=6}
par(mfrow=c(1,2))
hist(resid(mT_lm)) # normality
plot(mT_lm, which=2) # normality
par(mfrow=c(1,1))
```

The residuals are normal

### Check if some point are highly influential on the regression

```{r, fig.height=6}
par(mfrow=c(1,2))
plot(mT_lm, which=4) # leverage
plot(mT_lm, which=5) # leverage
par(mfrow=c(1,1))
```

Concerning Cook's distance and it's interpretation, some says that values below 1 are fine, other that value below 4/Observation number are fine.
Either case we are not too bad

### Check for homogeneity

```{r}
plot(mT_lm, which=1) # homogeneity
```


## ER~RH_T25 all data points (nls)


### model summary
```{r}
summary(mrh)
# lm_get_exp(mT_lm, details = "all")
```

### Check for normality of the residuals
```{r}
par(mfrow=c(1,2))
hist(df_mrh$resi)
qqnorm(df_mrh$resi)
qqline(df_mrh$resi)
par(mfrow=c(1,1))

plot(df_mrh$resi~df_mrh$predman)
```