---
title: "global GPP sat model"
author: "Benoît D'ANGELO"
date: "07/04/2015"
output:
  html_document:
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
---

<h3><a href="../CB_toc.html"> Carbon balance </a></h3>

***

```{r setup, echo=FALSE, message=FALSE}
rm(list=ls(all=TRUE))

library(laguettevarspa)
library(snoweather)
library(bdphdtoolbox)

# library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)

savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPPsat"
# Path to the project
proj_pth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG"

knitr::opts_chunk$set(fig.width=12,fig.height=8,echo=FALSE, warning=FALSE,message=FALSE)
options(width = 100)
```


```{r load data}
# Flux data calculated from get3F.R
T_levels <- c("Tair", "Tsurf", "T5", "T10", "T15", "T20", "T25", "T30", "T40", "T50", "T60", "T70", "T80", "T90", "T100")
# Flux data
flux_p7 <- file.path(proj_pth, "data", "processed", "flux_p7.csv")
df_GPP <- read.csv(flux_p7)%>%
  filter(F_type == "GPP")%>%
  mutate(date = as.Date(date),
         T_type = factor(T_type, levels = T_levels))

Temperature <- svTemperature %>%
  select(-date)

Ctrl <- svCtrlFact %>%
  select(ID_camp, placette, PAR_Deb, PAR_Fin, RH_m, WTL)%>%
  mutate(PAR = rowMeans(.[,3:4], na.rm=T))%>%
  select(ID_camp, placette, PAR, RH_m, WTL)

dfveg <- svVegetation %>%
  # group_by(ID_camp, placette)%>%
  filter(specie == "molinia")%>%
  mutate(area_m = mol_LtoS(height_m*10),
         area = area_m * number)%>%
  mutate(area = area/1000000, LAI = area/max(area), IV = LAI/max(LAI))%>%
  mutate(cover=as.numeric(as.character(cover)))%>%
  select(ID_camp, placette, number, area, LAI, IV, cover)
# dfveg$area <- ifelse(dfveg$number == 0, 0, dfveg$area)


df <- left_join(df_GPP, Temperature, by=c("ID_camp", "placette"))%>%
  left_join(., Ctrl, by=c("ID_camp", "placette"))%>%
  left_join(., dfveg, by=c("ID_camp", "placette"))%>%
  rename(netCO2F = flux)%>%
  filter(netCO2F > 0, PAR > 500) # remove value below 0 and light saturation data only
```


```{r functions}
pGPP_T <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~T25, xlab="température à -15 cm (°C)",ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# curve(a*exp(b*x), add=T, col="blue")
}

pmesmod <- function(X, ttl){
par(mar=c(4,4.5,.5,.5))
plot(netCO2F~predman, ylim=c(0,20), xlim=c(0,20),xlab=expression(paste("PBB modélisée (", mu, mol,m^-2,s^-1,")", sep=""))
, ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), main=ttl, data=X)
abline(a=0, b=1, col="black", lty=2)
text(19,20, "1:1", srt=45)
}

presmod <- function(X){
par(mar=c(4,4,.5,.5))
plot(resi~predman, xlab="valeurs prédites", ylab="résidus", data=X)
}
```

## GPP representation

According to <a href="../../relation_flux_T/GPP_T.html"> this document </a> the best ER representation with temperature at global scale is found by using an exponential model with -25 cm depth temperature.

# Temperature, ER~aexp-((T15-b)/c)


```{r calc mdl}
# Linear version ------------------------

# Non linear version --------------------
df_mJune <- df

mJune <- nls(netCO2F ~ a * exp(-((T15-b)/c)^2), data=df_mJune, start=list(a=10, b=10, c=10), na.action = na.exclude)

a <- coef(mJune)[1]
b <- coef(mJune)[2]
c <- coef(mJune)[3]

df_mJune$resi <- residuals(mJune)
df_mJune$pred <- predict(mJune)
# df_mJune$predman <- a*exp(b*df_mJune$T25)
df_mJune$predman <- a * exp(-((df_mJune$T15-b)/c)^2)

rmse_GPP_T15June <- sqrt(mean((df_mJune$predman-df_mJune$netCO2F)^2,na.rm=TRUE))
```


```{r, fig.height=6}
par(mfrow=c(1,2))
pGPP_T(df_mJune)
curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_mJune, "June")
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * exp(-((T15 - `r b`)/ `r c`)^2)

### diagnostic values

rmse = `r rmse_GPP_T15June` (nls)

aic = `r AIC(mJune)` (nls)

```{r exprt_fig, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "GPP_T15June_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJune)
curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_T15June_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJune, "June")
dev.off()
```

## Residual vs other controlling factors

```{r, fig.height=9}
par(mfrow=c(2,2))
plot(df_mJune$resi~df_mJune$WTL, main="vs. WTL") 
plot(df_mJune$resi~df_mJune$RH_m, main="vs. RH") 
plot(df_mJune$resi~df_mJune$area, main="vs. pseudoLAI", xlim=c(0,400000)) 
par(mfrow=c(1,1))
```



# Temperature, RH, ER~a * RH_m * exp-((T25-b)/c)

```{r calc mdl + IV}
# Linear version ------------------------

# Non linear version --------------------
df_mJuneRH <- df

mJuneRH <- nls(netCO2F ~ a * RH_m * exp(-((T15-b)/c)^2), data=df_mJuneRH, start=list(a=12, b=20, c=9), na.action = na.exclude)

a <- coef(mJuneRH)[1]
b <- coef(mJuneRH)[2]
c <- coef(mJuneRH)[3]

df_mJuneRH$resi <- residuals(mJuneRH)
df_mJuneRH$pred <- predict(mJuneRH)
# df_mJuneRH$predman <- a*exp(b*df_mJuneRH$T25)
df_mJuneRH$predman <- a * df_mJuneRH$RH_m * exp(-((df_mJuneRH$T15-b)/c)^2)

rmse_GPP_T15RHJune <- sqrt(mean((df_mJuneRH$predman-df_mJuneRH$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=6}
par(mfrow=c(1,2))
pGPP_T(df_mJuneRH)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_mJuneRH, "June")
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * RH_m * exp(-((T15 - `r b`)/ `r c`)^2)

### diagnostic values

rmse = `r rmse_GPP_T15RHJune` (nls)

aic = `r AIC(mJuneRH)` (nls)

```{r, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "GPP_T15RHJune_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJuneRH)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_T15RHJune_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJuneRH, "June")
dev.off()
```




# Temperature WTL, ER~a * WTL * exp-((T15-b)/c)

```{r}
# Linear version ------------------------

# Non linear version --------------------
df_mJuneWTL <- df

mJuneWTL <- nls(netCO2F ~ a * WTL * exp(-((T15-b)/c)^2), data=df_mJuneWTL, start=list(a=12, b=20, c=9), na.action = na.exclude)

a <- coef(mJuneWTL)[1]
b <- coef(mJuneWTL)[2]
c <- coef(mJuneWTL)[3]

df_mJuneWTL$resi <- residuals(mJuneWTL)
df_mJuneWTL$pred <- predict(mJuneWTL)
# df_mJuneWTL$predman <- a*exp(b*df_mJuneWTL$T25)
df_mJuneWTL$predman <- a * df_mJuneWTL$WTL * exp(-((df_mJuneWTL$T15-b)/c)^2)

rmse_GPP_T15WTLJune <- sqrt(mean((df_mJuneWTL$predman-df_mJuneWTL$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=6}
par(mfrow=c(1,2))
pGPP_T(df_mJuneWTL)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_mJuneWTL, "June")
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * RH_m * exp(-((T15 - `r b`)/ `r c`)^2)

### diagnostic values

rmse = `r rmse_GPP_T15WTLJune` (nls)

aic = `r AIC(mJuneWTL)` (nls)

```{r, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "GPP_T15WTLJune_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJuneWTL)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_T15WTLJune_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJuneWTL, "June")
dev.off()
```


# Temperature Veg, ER~a * ?? * exp-((T15-b)/c)

```{r}
# Linear version ------------------------

# Non linear version --------------------
df_mJunemolCOV <- df

mJunemolCOV <- nls(netCO2F ~ a * cover * exp(-((T15-b)/c)^2), data=df_mJunemolCOV, start=list(a=12, b=20, c=9), na.action = na.exclude)
# mJunemolCOV <- nls(netCO2F ~ a * area * exp(-((T15-b)/c)^2), data=df_mJunemolCOV, start=list(a=12, b=20, c=9), na.action = na.exclude, trace=T)

a <- coef(mJunemolCOV)[1]
b <- coef(mJunemolCOV)[2]
c <- coef(mJunemolCOV)[3]

df_mJunemolCOV$resi <- residuals(mJunemolCOV)
df_mJunemolCOV$pred <- predict(mJunemolCOV)
# df_mJunemolCOV$predman <- a*exp(b*df_mJunemolCOV$T25)
df_mJunemolCOV$predman <- a * df_mJunemolCOV$cover * exp(-((df_mJunemolCOV$T15-b)/c)^2)

rmse_GPP_T15molCOVJune <- sqrt(mean((df_mJunemolCOV$predman-df_mJunemolCOV$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=6}
par(mfrow=c(1,2))
pGPP_T(df_mJunemolCOV)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_mJunemolCOV, "June")
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * RH_m * exp(-((T15 - `r b`)/ `r c`)^2)

### diagnostic values

rmse = `r rmse_GPP_T15molCOVJune` (nls)

aic = `r AIC(mJunemolCOV)` (nls)

```{r, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "GPP_T15molCOVJune_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJunemolCOV)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_T15molCOVJune_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJunemolCOV, "June")
dev.off()
```







