---
title: "global ER model"
author: "Benoît D'ANGELO"
date: "07/04/2015"
output:
  html_document:
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
---

<h3><a href="../CB_toc.html"> Carbon balance </a></h3>

***

```{r setup, echo=FALSE, message=FALSE}
rm(list=ls(all=TRUE))

library(laguettevarspa)
library(snoweather)
library(bdphdtoolbox)

# library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)

savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/ER"

knitr::opts_chunk$set(fig.width=12,fig.height=8,echo=FALSE, warning=FALSE,message=FALSE)
options(width = 100)
```


```{r load data}
# Fichier VS -- Données ponctuelles
## Flux
dfER <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/3F_data.csv") %>%
  filter(F_type == "ER")%>%
  rename(netCO2F=flux)%>%
  select(date, ID_camp, placette, netCO2F)

## Vegetation
dfveg <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/svIVcov.csv") %>%
  select(ID_camp, placette, H, IVcov, IVcov_area)
# dfveg <- svVegetation %>%
#   group_by(ID_camp, placette)%>%
#   filter(specie == "molinia")%>%
#   mutate(area_m = mol_LtoS(height_m*10),
#          area = area_m * number,
#          cover = as.numeric(as.character(cover)))%>%
#   select(ID_camp, placette, cover, number, area)
# dfveg$area <- ifelse(dfveg$number == 0, 0, dfveg$area)

## Ctrl facteur
dfctrl <- svCtrlFact %>%
  select(ID_camp, placette, WTL, RH_m)

## Soil temperature
dfT <- svTemperature %>%
  select(ID_camp, placette,Tair, T5, T10, T15, T20, T25)

## Merge all
# données ponctuelles
df_all <- dfER %>%
  left_join(., dfT, by=c("ID_camp", "placette"))%>%
  left_join(., dfctrl, by=c("ID_camp", "placette"))%>%
  left_join(., dfveg, by=c("ID_camp", "placette"))

# données moyennées
df <- df_all %>%
  group_by(ID_camp)%>%
  summarise(netCO2F=mean(netCO2F, na.rm=T),
            Tair=mean(Tair, na.rm=T),
            T5=mean(T5, na.rm=T),
            T10=mean(T10, na.rm=T),
            T15=mean(T15, na.rm=T),
            T20=mean(T20, na.rm=T),
            T25=mean(T25, na.rm=T),
            WTL=mean(WTL, na.rm=T),
            RH_m=mean(RH_m, na.rm=T),
            H=mean(H, na.rm=T),
            IVcov=mean(IVcov, na.rm=T),
            IVcov_area=mean(IVcov_area, na.rm=T)
            )

```


```{r functions}
pER_T <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~T25, xlab="température à -25 cm (°C)",ylab=expression(paste("Re mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# curve(a*exp(b*x), add=T, col="blue")
}
pER_Tair <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~Tair, xlab="température de l'air (°C)",ylab=expression(paste("Re mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# curve(a*exp(b*x), add=T, col="blue")
}

pmesmod <- function(X){
par(mar=c(4,4.5,.5,.5))
plot(netCO2F~predman, ylim=c(0,20), xlim=c(0,20),xlab=expression(paste("Re modélisée (", mu, mol,m^-2,s^-1,")", sep=""))
, ylab=expression(paste("Re mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
abline(a=0, b=1, col="black", lty=2)
text(19,20, "1:1", srt=45)
}

presmod <- function(X){
par(mar=c(4,4,.5,.5))
plot(resi~predman, xlab="valeurs prédites", ylab="résidus", data=X)
}
```


# ER representation

According to <a href="../../relation_flux_T/ER_T.html"> this document </a> the best ER representation with temperature at global scale is found by using an exponential model with -25 cm depth temperature.

# Temperature, ER~aexp(bTair)

```{r calc mdl}
df_mT <- df

# Linear version ------------------------
# mT <- lm(log(netCO2F)~Tair, data = df_mT, na.action = na.exclude)
# summary(mT)
# a <- exp(coef(mT)[1]) # a <- 0.3400943 
# b <- coef(mT)[2]      # b <- 0.1034424
# 
# # Attention à la linéarisation
# devmean <- log(df_mT$netCO2F)-(mean(log(df_mT$netCO2F))) # deviation à la moyenne
# 
# # Calcul résidus
# df_mT$resi <- residuals(mT)
# df_mT$predman <- a*exp(b*df_mT$Tair)
# # Si calcul du R2 sur données dé-transformée : R2=0.9
# # Calcul manuel du R2
# SSres <-sum(df_mT$resi^2) # Total sum of squares
# SStot <- sum(devmean^2) # Residual sum of squares
# # 2 way to calculate
# R2 <- (SStot-SSres)/SStot 
# R2 <- 1 - SSres/SStot
# # Adjusted R2
# N <- NROW(devmean) # sample size
# p <- 1 # number of predictors
# R2a <- 1-((1-R2)*(N-1))/(N-p-1)
# 
# rmse <- sqrt(mean((df_mT$predman-df_mT$netCO2F)^2,na.rm=TRUE))


# Non linear version --------------------
mT <- nls(netCO2F ~ a * exp(b*Tair), data=df_mT, start=list(a=0.3, b=0.1), na.action = na.exclude)
a <- coef(mT)[1] # a <- 0.3766245
b <- coef(mT)[2] # b <- 0.1006095

devmean <- df_mT$netCO2F-(mean(df_mT$netCO2F)) # deviation à la moyenne

## Calcul résidus
### automatique
df_mT$resi <- residuals(mT)
### manuel
df_mT$predman <- a*exp(b*df_mT$Tair)
df_mT$resiman <- df_mT$netCO2F-df_mT$predman

# Calcul manuel R2 ----------------------
## resi et resiman : resultats identiques
SSres <-sum(df_mT$resiman^2) # Total sum of squares
SStot <- sum(devmean^2) # Residual sum of squares
# 2 way to calculate
R2 <- (SStot-SSres)/SStot 
R2 <- 1 - SSres/SStot
# Adjusted R2
N <- NROW(devmean) # sample size
p <- 1 # number of predictors
R2a <- 1-((1-R2)*(N-1))/(N-p-1)


# Autre indicateurs ---------------------
Q10 <- exp(10*b)
rmse <- sqrt(mean((df_mT$predman-df_mT$netCO2F)^2,na.rm=TRUE))

# prediction sur valeurs ponctuelles ----
df_all$predman <- a*exp(b*df_all$Tair)
df_all$resi <- df_all$netCO2F-df_all$predman
```

```{r, fig.height=4}
## Valeurs moyennes
par(mfrow=c(1,3))
pER_Tair(df_mT)
curve(a*exp(b*x), add=T, col="blue")
pmesmod(df_mT)
presmod(df_mT)
par(mfrow=c(1,1))
## Valeurs ponctuelles
par(mfrow=c(1,3))
pER_Tair(df_all)
curve(a*exp(b*x), add=T, col="blue")
pmesmod(df_all)
presmod(df_all)
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * exp(`r b` * Tair)

R2 = `r R2a` (lm)

rmse = `r rmse` (lm)

aic = `r AIC(mT)` (lm)

```{r exprt_fig, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "avgER_Tair_ecosyt.pdf"), width=6.5, height=5)
pER_T(df_mT)
curve(a*exp(b*x), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "avgER_Tair_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mT)
dev.off()


cairo_pdf(file.path(savpth, "avgER_Tair_ecosyt_resmod.pdf"), width=5, height=5)
presmod(df_mT)
dev.off()
```




## Residual vs other controlling factors

```{r, fig.height=4}
par(mfrow=c(1,3))
plot(df_mT$resi~df_mT$WTL, main="vs. WTL") 
plot(df_mT$resi~df_mT$RH_m, main="vs. RH") 
plot(df_mT$resi~df_mT$IVcov, main="vs. IVcov") 
par(mfrow=c(1,1))
par(mfrow=c(1,3))
plot(df_all$resi~df_all$WTL, main="vs. WTL") 
plot(df_all$resi~df_all$RH_m, main="vs. RH") 
plot(df_all$resi~df_all$IVcov, main="vs. IVcov") 
par(mfrow=c(1,1))
```

# Temperature and IV ER~a*exp(b*Tair)+c*IVcov

```{r}
df_mTIV <- df

# Non linear version --------------------
# mTIV <- nls(netCO2F ~ a * exp(b*Tair) + c * IVcov, data=df_mTIV, start=list(a=0.3, b=0.1, c=1), na.action = na.exclude)
mTIV <- nls(netCO2F ~ (a*IVcov + c) * exp(b*Tair), data=df_mTIV, start=list(a=0.3, b=0.1, c=1), na.action = na.exclude)
a <- coef(mTIV)[1] # a <- 0.3766245
b <- coef(mTIV)[2] # b <- 0.1006095
c <- coef(mTIV)[3] # b <- 0.1006095


devmean <- df_mTIV$netCO2F-(mean(df_mTIV$netCO2F)) # deviation à la moyenne

## Calcul résidus
### automatique
df_mTIV$resi <- residuals(mTIV)
### manuel
# df_mTIV$predman <- a*exp(b*df_mTIV$Tair)+c*df_mTIV$IVcov
df_mTIV$predman <- (a*df_mTIV$IVcov + c)*exp(b*df_mTIV$Tair)
df_mTIV$resiman <- df_mTIV$netCO2F-df_mTIV$predman

# Calcul manuel R2 ----------------------
## resi et resiman : resultats identiques
SSres <-sum(df_mTIV$resiman^2) # Total sum of squares
SStot <- sum(devmean^2) # Residual sum of squares
# 2 way to calculate
R2 <- (SStot-SSres)/SStot 
R2 <- 1 - SSres/SStot
# Adjusted R2
N <- NROW(devmean) # sample size
p <- 1 # number of predictors
R2a <- 1-((1-R2)*(N-1))/(N-p-1)


# Autre indicateurs ---------------------
Q10 <- exp(10*b)
rmse <- sqrt(mean((df_mTIV$predman-df_mTIV$netCO2F)^2,na.rm=TRUE))

# prediction sur valeurs ponctuelles ----
# df_all$predman <- a*exp(b*df_all$Tair)
df_all$predman <- (a*df_all$IVcov + c)*exp(b*df_all$Tair)
df_all$resi <- df_all$netCO2F-df_all$predman
```

### model equation

ER = `r a` * exp(`r b` * Tair) + c * IVcov

R2 = `r R2a` (lm)

rmse = `r rmse` (lm)

aic = `r AIC(mTIV)` (lm)


```{r, fig.height=4}
par(mfrow=c(1,3))
pER_Tair(df_mTIV)
pmesmod(df_mTIV)
presmod(df_mTIV)
par(mfrow=c(1,1))
par(mfrow=c(1,3))
pER_Tair(df_all)
pmesmod(df_all)
presmod(df_all)
par(mfrow=c(1,1))
```

## Residual vs other controlling factors

```{r, fig.height=4}
par(mfrow=c(1,3))
plot(df_mTIV$resi~df_mTIV$WTL, main="vs. WTL") 
plot(df_mTIV$resi~df_mTIV$RH_m, main="vs. RH") 
plot(df_mTIV$resi~df_mTIV$IVcov, main="vs. IVcov") 
par(mfrow=c(1,1))
par(mfrow=c(1,3))
plot(df_all$resi~df_all$WTL, main="vs. WTL") 
plot(df_all$resi~df_all$RH_m, main="vs. RH") 
plot(df_all$resi~df_all$IVcov, main="vs. IVcov") 
par(mfrow=c(1,1))
```




***
***
***

# Diagnostic plot
