---
title: "global GPP sat model"
author: "Benoît D'ANGELO"
date: "07/04/2015"
output:
  html_document:
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
---

<h3><a href="../CB_toc.html"> Carbon balance </a></h3>

***

```{r setup, echo=FALSE, message=FALSE}
rm(list=ls(all=TRUE))

library(laguettevarspa)
library(snoweather)
library(bdphdtoolbox)

# library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)

savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/carbonbalance/ecosyst/GPPsat"
# Path to the project
proj_pth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG"

knitr::opts_chunk$set(fig.width=12,fig.height=8,echo=FALSE, warning=FALSE,message=FALSE)
options(width = 100)
```


```{r load data}
# Fichier VS -- Données ponctuelles
## Flux
dfGPP <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/3F_data.csv") %>%
  filter(F_type == "GPP")%>%
  rename(netCO2F=flux)%>%
  select(date, ID_camp, placette, netCO2F)

## Vegetation
dfveg <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/svIVcov.csv") %>%
  select(ID_camp, placette, IVcov, IVcov_area)
# dfveg <- svVegetation %>%
#   group_by(ID_camp, placette)%>%
#   filter(specie == "molinia")%>%
#   mutate(area_m = mol_LtoS(height_m*10),
#          area = (area_m * number)/1000000, # conversion m2
#          LAI = area/max(area, na.rm=T),
#          cover = as.numeric(as.character(cover)))%>%
#   select(ID_camp, placette, cover, number, area)
# dfveg$area <- ifelse(dfveg$number == 0, 0, dfveg$area)

## Ctrl facteur
dfctrl <- svCtrlFact %>%
  select(ID_camp, placette, PAR_Deb, PAR_Fin, WTL, RH_m)%>%
  mutate(PAR = rowMeans(.[,3:4], na.rm=T))%>%
  select(ID_camp, placette, PAR, RH_m, WTL)

## Soil temperature
dfT <- svTemperature %>%
  select(ID_camp, placette, Tair, T5, T10, T15, T20, T25, T30)

## Merge all
# données ponctuelles
df_all <- dfGPP %>%
  left_join(., dfT, by=c("ID_camp", "placette"))%>%
  left_join(., dfctrl, by=c("ID_camp", "placette"))%>%
  left_join(., dfveg, by=c("ID_camp", "placette"))%>%
  filter(netCO2F > 0, PAR > 500) # remove value below 0 and light saturation data only

# données moyennées
df <- df_all %>%
  group_by(ID_camp)%>%
  summarise(netCO2F=mean(netCO2F, na.rm=T),
            Tair=mean(Tair, na.rm=T),
            T5=mean(T5, na.rm=T),
            T10=mean(T10, na.rm=T),
            T15=mean(T15, na.rm=T),
            T20=mean(T20, na.rm=T),
            T25=mean(T25, na.rm=T),
            T30=mean(T30, na.rm=T),
            PAR=mean(PAR, na.rm=T),
            WTL=mean(WTL, na.rm=T),
            RH_m=mean(RH_m, na.rm=T),
            # H=mean(H, na.rm=T),
            IVcov=mean(IVcov, na.rm=T),
            IVcov_area=mean(IVcov_area, na.rm=T)
            )

```


```{r functions}
pGPP_T <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~T25, xlab="température à -15 cm (°C)",ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# curve(a*exp(b*x), add=T, col="blue")
}

pGPP_Tair <- function(X){
par(mar=c(5.1,5.1,2.1,2.1))
plot(netCO2F~Tair, xlab="température de l'air (°C)",ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
# curve(a*exp(b*x), add=T, col="blue")
}

pmesmod <- function(X){
par(mar=c(4,4.5,.5,.5))
plot(netCO2F~predman, ylim=c(0,20), xlim=c(0,20),xlab=expression(paste("PBB modélisée (", mu, mol,m^-2,s^-1,")", sep=""))
, ylab=expression(paste("PBB mesurée (", mu, mol,m^-2,s^-1,")", sep="")), data=X)
abline(a=0, b=1, col="black", lty=2)
text(19,20, "1:1", srt=45)
}

presmod <- function(X){
par(mar=c(4,4,.5,.5))
plot(resi~predman, xlab="valeurs prédites", ylab="résidus", data=X)
}
```

## GPP representation

According to <a href="../../relation_flux_T/GPP_T.html"> this document </a> the best ER representation with temperature at global scale is found by using an exponential model with -25 cm depth temperature.

# Temperature, ER~aexp-((Tair-b)/c)


```{r calc mdl}
# Linear version ------------------------
df_mT_lm <- df
#test exp
mT_lm <- lm(log(netCO2F)~Tair, data = df_mT_lm, na.action = na.exclude)
summary(mT_lm)
# mT_lm <- lm(log(netCO2F)~T5, data = df_mT_lm, na.action = na.exclude)
summary(mT_lm)

a <- exp(coef(mT_lm)[1])
b <- coef(mT_lm)[2]
Q10 <- exp(10*b)

df_mT_lm$resi <- residuals(mT_lm)
df_mT_lm$pred <- predict(mT_lm)
df_mT_lm$predman <- a*exp(b*df_mT_lm$Tair)
# df_mT_lm$predman <- a*exp(b*df_mT_lm$T5)

rmse_ER_T25_lm <- sqrt(mean((df_mT_lm$predman-df_mT_lm$netCO2F)^2,na.rm=TRUE))

# Non linear version --------------------
df_mJune <- df

mJune <- nls(netCO2F ~ a * exp(-((Tair-b)/c)^2), data=df_mJune, start=list(a=20, b=30, c=10), na.action = na.exclude)
# mJune <- nls(netCO2F ~ a * exp(-((T15-b)/c)^2), data=df_mJune, start=list(a=10, b=10, c=10), na.action = na.exclude)


a <- coef(mJune)[1]
b <- coef(mJune)[2]
c <- coef(mJune)[3]

df_mJune$resi <- residuals(mJune)
df_mJune$pred <- predict(mJune)
df_mJune$predman <- a * exp(-((df_mJune$Tair-b)/c)^2)

df_all$predman <- a * exp(-((df_all$Tair-b)/c)^2)
df_all$resi <- df_all$netCO2F - df_all$predman

# Calcul manuel du R2
# Attention à la linéarisation
devmean <- df_mJune$netCO2F-(mean(df_mJune$netCO2F)) # deviation à la moyenne
SSres <-sum(df_mJune$resi^2) # Total sum of squares
SStot <- sum(devmean^2) # Residual sum of squares
# 2 way to calculate
R2 <- (SStot-SSres)/SStot 
R2 <- 1 - SSres/SStot
# Adjusted R2
N <- NROW(devmean) # sample size
p <- 1 # number of predictors
R2a <- 1-((1-R2)*(N-1))/(N-p-1)

rmse_GPP_T15June <- sqrt(mean((df_mJune$predman-df_mJune$netCO2F)^2,na.rm=TRUE))
```


```{r, fig.height=4}
par(mfrow=c(1,3))
pGPP_Tair(df_mJune)
curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_mJune)
presmod(df_mJune)
par(mfrow=c(1,1))

par(mfrow=c(1,3))
pGPP_Tair(df_all)
curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_all)
presmod(df_all)
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * exp(-((T15 - `r b`)/ `r c`)^2)

### diagnostic values

rmse = `r rmse_GPP_T15June` (nls)

aic = `r AIC(mJune)` (nls)

```{r exprt_fig, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "GPP_T15June_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJune)
curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairJune_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJune)
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairJune_ecosyt_resmod.pdf"), width=5, height=5)
presmod(df_mJune)
dev.off()
```

## Residual vs other controlling factors

```{r, fig.height=4}
par(mfrow=c(1,3))
plot(df_mJune$resi~df_mJune$WTL, main="vs. WTL") 
plot(df_mJune$resi~df_mJune$RH_m, main="vs. RH") 
plot(df_mJune$resi~df_mJune$IVcov, main="vs. IV cov")
par(mfrow=c(1,1))

par(mfrow=c(1,3))
plot(df_all$resi~df_all$WTL, main="vs. WTL") 
plot(df_all$resi~df_all$RH_m, main="vs. RH") 
plot(df_all$resi~df_all$IVcov, main="vs. IV cov")
par(mfrow=c(1,1))
```



# Temperature, RH, ER~a * RH_m * exp-((T25-b)/c)

```{r calc mdl + RH, eval=FALSE}
# Linear version ------------------------

# Non linear version --------------------
df_mJuneRH <- df

mJuneRH <- nls(netCO2F ~ a * RH_m * exp(-((Tair-b)/c)^2), data=df_mJuneRH, start=list(a=12, b=20, c=9), na.action = na.exclude)

a <- coef(mJuneRH)[1]
b <- coef(mJuneRH)[2]
c <- coef(mJuneRH)[3]

df_mJuneRH$resi <- residuals(mJuneRH)
df_mJuneRH$pred <- predict(mJuneRH)
# df_mJuneRH$predman <- a*exp(b*df_mJuneRH$T25)
df_mJuneRH$predman <- a * df_mJuneRH$RH_m * exp(-((df_mJuneRH$Tair-b)/c)^2)

rmse_GPP_T15RHJune <- sqrt(mean((df_mJuneRH$predman-df_mJuneRH$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=4, eval=FALSE}
par(mfrow=c(1,3))
pGPP_T(df_mJuneRH)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_mJuneRH)
presmod(df_mJuneRH)
par(mfrow=c(1,1))
```

### model equation

ER = a * RH_m * exp(-((Tair - a)/ c`)^2)

### diagnostic values

rmse =  (nls)

aic = (nls)

```{r, error=FALSE, results="hide", eval=FALSE}
cairo_pdf(file.path(savpth, "GPP_TairRHJune_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJuneRH)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairRHJune_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJuneRH)
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairRHJune_ecosyt_nesmod.pdf"), width=5, height=5)
presmod(df_mJuneRH)
dev.off()
```




# Temperature WTL, ER~a * WTL * exp-((Tair-b)/c)

```{r}
# Linear version ------------------------

# Non linear version --------------------
df_mJuneWTL <- df

mJuneWTL <- nls(netCO2F ~ a * WTL * exp(-((Tair-b)/c)^2), data=df_mJuneWTL, start=list(a=12, b=20, c=9), na.action = na.exclude)

a <- coef(mJuneWTL)[1]
b <- coef(mJuneWTL)[2]
c <- coef(mJuneWTL)[3]

df_mJuneWTL$resi <- residuals(mJuneWTL)
df_mJuneWTL$pred <- predict(mJuneWTL)
# df_mJuneWTL$predman <- a*exp(b*df_mJuneWTL$T25)
df_mJuneWTL$predman <- a * df_mJuneWTL$WTL * exp(-((df_mJuneWTL$Tair-b)/c)^2)

# Calcul manuel du R2
# Attention à la linéarisation
devmean <- df_mJuneWTL$netCO2F-(mean(df_mJuneWTL$netCO2F)) # deviation à la moyenne
SSres <-sum(df_mJuneWTL$resi^2) # Total sum of squares
SStot <- sum(devmean^2) # Residual sum of squares
# 2 way to calculate
R2 <- (SStot-SSres)/SStot 
R2 <- 1 - SSres/SStot
# Adjusted R2
N <- NROW(devmean) # sample size
p <- 1 # number of predictors
R2a <- 1-((1-R2)*(N-1))/(N-p-1)


rmse_GPP_T15WTLJune <- sqrt(mean((df_mJuneWTL$predman-df_mJuneWTL$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=4}
par(mfrow=c(1,3))
pGPP_T(df_mJuneWTL)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
pmesmod(df_mJuneWTL)
presmod(df_mJuneWTL)
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * RH_m * exp(-((Tair - `r b`)/ `r c`)^2)

### diagnostic values

rmse = `r rmse_GPP_T15WTLJune` (nls)

aic = `r AIC(mJuneWTL)` (nls)

```{r, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "GPP_TairWTLJune_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJuneWTL)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairWTLJune_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJuneWTL)
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairWTLJune_ecosyt_resmod.pdf"), width=5, height=5)
presmod(df_mJuneWTL)
dev.off()
```


# Temperature Veg, ER~a * IVcov * exp-((T15-b)/c)

```{r}
# Linear version ------------------------

# Non linear version --------------------
df_mJunemolCOV <- df

mJunemolCOV <- nls(netCO2F ~ a * IVcov * exp(-((Tair-b)/c)^2), data=df_mJunemolCOV, start=list(a=12, b=20, c=9), na.action = na.exclude)
# mJunemolCOV <- nls(netCO2F ~ a * area * exp(-((T15-b)/c)^2), data=df_mJunemolCOV, start=list(a=12, b=20, c=9), na.action = na.exclude, trace=T)

a <- coef(mJunemolCOV)[1]
b <- coef(mJunemolCOV)[2]
c <- coef(mJunemolCOV)[3]

df_mJunemolCOV$resi <- residuals(mJunemolCOV)
df_mJunemolCOV$pred <- predict(mJunemolCOV)
# df_mJunemolCOV$predman <- a*exp(b*df_mJunemolCOV$T25)
df_mJunemolCOV$predman <- a * df_mJunemolCOV$IVcov * exp(-((df_mJunemolCOV$Tair-b)/c)^2)

df_all$predman <- a * df_all$IVcov * exp(-((df_all$Tair-b)/c)^2)
df_all$resi <- df_all$netCO2F-df_all$predman

# Calcul manuel du R2
# Attention à la linéarisation
devmean <- df_mJunemolCOV$netCO2F-(mean(df_mJunemolCOV$netCO2F)) # deviation à la moyenne
SSres <-sum(df_mJunemolCOV$resi^2) # Total sum of squares
SStot <- sum(devmean^2) # Residual sum of squares
# 2 way to calculate
R2 <- (SStot-SSres)/SStot 
R2 <- 1 - SSres/SStot
# Adjusted R2
N <- NROW(devmean) # sample size
p <- 1 # number of predictors
R2a <- 1-((1-R2)*(N-1))/(N-p-1)


rmse_GPP_T15molCOVJune <- sqrt(mean((df_mJunemolCOV$predman-df_mJunemolCOV$netCO2F)^2,na.rm=TRUE))
```

```{r, fig.height=4}
par(mfrow=c(1,3))
pGPP_T(df_mJunemolCOV)
pmesmod(df_mJunemolCOV)
presmod(df_mJunemolCOV)
par(mfrow=c(1,1))

par(mfrow=c(1,3))
pGPP_T(df_all)
pmesmod(df_all)
presmod(df_all)
par(mfrow=c(1,1))
```

### model equation

ER = `r a` * IVcov * exp(-((Tair - `r b`)/ `r c`)^2)

### diagnostic values

rmse = `r rmse_GPP_T15molCOVJune` (nls)

aic = `r AIC(mJunemolCOV)` (nls)

```{r, error=FALSE, results="hide"}
cairo_pdf(file.path(savpth, "GPP_TairIVCOVJune_ecosyt.pdf"), width=6.5, height=5)
pGPP_T(df_mJunemolCOV)
# curve(a*exp(-((x-b)/c)^2), add=T, col="blue")
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairIVCOVJune_ecosyt_mesmod.pdf"), width=5, height=5)
pmesmod(df_mJunemolCOV)
dev.off()

cairo_pdf(file.path(savpth, "GPP_TairIVCOVJune_ecosyt_resmod.pdf"), width=5, height=5)
presmod(df_mJunemolCOV)
dev.off()
```







