---
title: "Temperatures"
author: "Benoît D'ANGELO"
date: "23/02/2015"
output:
  html_document:
    fig_height: 7
    fig_width: 9
    includes:
      in_header: ../../in_header.html
    theme: flatly
    toc: yes
---
<h3><a href="../vis_toc.html"> Visualisation </a></h3>
  
***
```{r, echo=FALSE, message=FALSE}
rm(list=ls())
library(laguettevarspa)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales) # access to break/formatting fn

savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/visualisation"
```


```{r, echo=FALSE}
df <- svTemperature %>%
  select(ID_camp, placette, date, Tair, Tsurf, T5, T10, T15, T20, T25, T30,
         T40, T50, T60, T70, T80, T90, T100)%>%
  mutate(ID_camp=as.factor(ID_camp))%>%
  gather("profondeur", "temperature", 4:18)%>%
  separate(date, c("year","month", "day"),remove = F)

# Order levels
df$profondeur <- with(df, factor(profondeur, levels = rev(levels(profondeur))))

dfT <- df %>%
  group_by(year, month, profondeur) %>%
  summarise(T_sd = sd(temperature, na.rm=T), temperature = mean(temperature, na.rm=T))

dfT <- as.data.frame(dfT)
```

## Temperature evolution

```{r, echo=FALSE,warning=FALSE}
ggplot(df, aes(x=temperature, y=profondeur, group=ID_camp, color=ID_camp))+
  geom_point()+
  facet_wrap(~placette)+
  theme_bw()
```

## Temperature monthly evolution (selected depth)

```{r, echo=FALSE}
dfTs <- filter(dfT, profondeur %in% c("Tair", "T10", "T15","T30", "T100") & year!=2015)

ggplot(dfTs, aes(x=month, y=temperature, color = profondeur))+
  geom_point()+
  geom_line(aes(group=profondeur))+
  facet_wrap(~year)+
  theme_bw()
```

## Temperature standard deviation per year

```{r, echo=FALSE}
dfP <- df %>%
  group_by(year, profondeur) %>%
  filter(year != 2015) %>%
  summarise(T_sd = sd(temperature, na.rm=T), temperature = mean(temperature, na.rm=T))

ggplot(dfP, aes(x=T_sd, y=profondeur))+
  geom_point()+
#   geom_line(aes(group=profondeur))+
  facet_wrap(~year)+
  theme_bw()
```



## Mean Tair

```{r, echo=FALSE, warning=FALSE, fig.width=9}

T_mean_evolution <- function(profond="Tair", y_lab="température de l'air (°C)"){
  dfm <- df %>%
  group_by(ID_camp)%>%
  filter(profondeur == profond)%>%
  summarise(date=min(date),
            year=unique(year),
            T_sd=sd(temperature, na.rm=T),
            temperature=mean(temperature, na.rm=T)
            )
  
  ggplot(dfm, aes(x=date, y=temperature))+
  geom_point(size=3)+
  geom_linerange(aes(x=date, ymin=temperature-T_sd, ymax=temperature+T_sd))+
  labs(y=y_lab)+
  theme_bw()+
  theme(strip.text.x = element_text(size = 14),
        axis.text=element_text(size=14),
        panel.grid.major.x = element_blank(), # DIAPO
        panel.grid.major.y = element_line(size=.05, colour="gray95"),
        panel.grid.minor = element_blank())
}

```

```{r, echo=FALSE, warning=FALSE, fig.width=9, fig.height=5}
T_mean_evolution("Tair", "température de l'air (°C)")
ggsave("Tair_mean_evolution.pdf", path=savpth)
T_mean_evolution("T5", "température du sol à -5 cm (°C)")
ggsave("T5_mean_evolution.pdf", path=savpth)
```

```{r, echo=FALSE, warning=FALSE, fig.width=9, fig.height=12}
dfm <- df %>%
  filter(profondeur %in% c("Tair","T5", "T30", "T50", "T100"))%>%
  # filter(profondeur %in% c("Tair", "Tsurf", "T5", "T10", "T30", "T50", "T100"))%>%
  group_by(ID_camp, profondeur)%>%
  summarise(date=min(date),
            year=unique(year),
            T_sd=sd(temperature, na.rm=T),
            temperature=mean(temperature, na.rm=T)
            )

dfm <- within(dfm, profondeur <- ordered(profondeur, levels = rev(sort(unique(profondeur)))))
  
  ggplot(dfm, aes(x=date, y=temperature))+
  geom_point(size=3)+
  geom_linerange(aes(x=date, ymin=temperature-T_sd, ymax=temperature+T_sd))+
  labs(y="temperatures (°C)", x="2013 - 2014")+
  scale_x_date(breaks = date_breaks("2 months"), labels = date_format("%b"))+
  facet_grid(profondeur~.)+
  theme_bw()+
  theme(strip.text.x = element_text(size = 14),
        axis.text=element_text(size=14),
        panel.grid.major.x = element_blank(), # DIAPO
        panel.grid.major.y = element_line(size=.05, colour="gray95"),
        panel.grid.minor = element_blank())

ggsave("T_mean_evolution.pdf", path=savpth)
