---
title: "GPP relations with environmental variables"
author: "Benoît D'ANGELO"
date: "14 avril 2016"
output:
  html_document:
    code_folding: hide
    fig_height: 3
    fig_width: 7
    includes:
      in_header: ../in_header.html
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: true
---

<h3><a href="../cor_toc.html"> Relation fluxes/variables environnementale </a></h3>

# Setup

## Load packages and set paths

```{r, message=FALSE}
# File name : /2013_spavar_LG/report/rel_flux_envir/cor_GPP.Rmd
rm(list=ls(all=TRUE)) # Clean start

# Homemade packages (see "Howto" page to install them)
library(bdphdtoolbox) # Personal toolbox

# CRAN packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(scales)

# Folder to save graphes
savpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/graphs/visualisation"

# Folder to save data treatement
outpth <- "/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed"

# allow wider tables and graphes in html output
options(width = 100)

# Load custom color set
source("../../src/report/custom_colors.R")
# source("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/src/report/custom_colors.R")
```

## Load and transform data

```{r load_data}
# Load treated data (generated with getClean_fluxesFC)
dfges <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC.csv")%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))
  
# Load treated data (generated with getClean_fluxesFC)
# Campaign averages
dfgesm <- read.csv("/home/dangelo/Documents/4.ScienceStuff/2.Projects/2013_spaVar_LG/data/processed/cl_fluxesFC_avg.csv")%>%
  mutate(timestamp=as.POSIXct(as.character(timestamp)))%>%
  mutate(date=as.POSIXct(as.character(date)))
```

# GPP vs environmental variable 

## Correlation matrix {.tabset}

### Vegetation and Water table level

```{r, fig.height=8, fig.width=8}
# dfges dfgesm
sel <- dfgesm %>%
  select(GPP, A, H, M, IVcov, WTL)
pairs(sel, lower.panel = panel_cor, cex.labels = 2) # panel_cor function from bdphdtoolbox
```

With:

* A : Shrub layer cover in percentage (fr: Arbuste)
* H : Herbs layer cover in percentage (fr: Herabacées)
* M : Mosses layer cover in percentage (fr: Mousses)

### Temperatures

```{r, fig.height=8, fig.width=8}
sel <- dfgesm %>%
  select(GPP,Tair, T5, T10, T20, T30, T40, T50, T60, T70, T80)
pairs(sel, lower.panel = panel_cor, cex.labels = 2)
```

## GPP vs temperature: R2 evolution with depth

Using GPP=a*exp(b*Temperature)

```{r, fig.width=5, fig.height=7}
t <- dfgesm %>%
  select(GPP, WTL, A, H, M, IVcov, Tair, T5, T10, T20, T30, T40, T50, T60, T70, T80, T90)

# plot(t$GPP~t$T50)
# summary(lm(t$GPP~t$T40))
R1 <- summary(lm(log(t$GPP)~t$Tair))$r.squared
R2 <- summary(lm(log(t$GPP)~t$T5))$r.squared
R3 <- summary(lm(log(t$GPP)~t$T10))$r.squared
R4 <- summary(lm(log(t$GPP)~t$T20))$r.squared
R5 <- summary(lm(log(t$GPP)~t$T30))$r.squared
R6 <- summary(lm(log(t$GPP)~t$T40))$r.squared
R7 <- summary(lm(log(t$GPP)~t$T50))$r.squared
R8 <- summary(lm(log(t$GPP)~t$T60))$r.squared
R9 <- summary(lm(log(t$GPP)~t$T70))$r.squared
R10 <- summary(lm(log(t$GPP)~t$T80))$r.squared
R11 <- summary(lm(log(t$GPP)~t$T90))$r.squared
# summary(lm(log(t$GPP)~t$T100))$r.squared

p <- data.frame(prof=c(10, -5, -10, -20, -30, -40, -50, -60, -70, -80, -90),
                R2=c(R1, R2, R3, R4, R5, R6, R7, R8, R9, R10, R11))

ggplot(p, aes(x=R2, y=prof))+
  annotate("rect", xmin=-Inf, xmax=Inf, ymin=-18.2, ymax=-5.1, fill = lbleu)+
  annotate("rect", xmin=-Inf, xmax=Inf, ymin=-9.2, ymax=-7.1, fill = dbleu)+
  geom_point(size=3, color=gris)+
  geom_hline(yintercept = 0, linetype="dashed", color=lgris)+
  annotate("text", x=0.75, y=-3.2, label="nappe", color=bleu)+
  annotate("text", x=0.67, y=2, label="surface du sol", color=gris)+
  labs(x=expression(R^2), y="profondeur (en cm)")+
  theme_classic()+
  theme(plot.margin=unit(c(1,1,0,0),"mm"))
ggsave("GPP_T_exp.pdf", path=savpth, width=3.5, height=5)
```

## GPP vs vegetation and water table level


```{r}
lin_A <- round(summary(lm(t$GPP~t$A))$r.squared,2)
lin_H <- round(summary(lm(t$GPP~t$H))$r.squared,2)
lin_M <- round(summary(lm(t$GPP~t$M))$r.squared,2)
lin_IVcov <- round(summary(lm(t$GPP~t$IVcov))$r.squared,2)
lin_WTL <- round(summary(lm(t$GPP~t$WTL))$r.squared,2)

exp_A <- round(summary(lm(log(t$GPP)~t$A))$r.squared,2)
exp_H <- round(summary(lm(log(t$GPP)~t$H))$r.squared,2)
exp_M <- round(summary(lm(log(t$GPP)~t$M))$r.squared,2)
exp_IVcov <- round(summary(lm(log(t$GPP)~t$IVcov))$r.squared,2)
exp_WTL <- round(summary(lm(log(t$GPP)~t$WTL))$r.squared,2)

linexp <- data.frame(equation=c("lin", "exp"),
                     A=c(lin_A, exp_A),
                     H=c(lin_H, exp_H),
                     M=c(lin_M, exp_M),
                     IVcov=c(lin_IVcov, exp_IVcov),
                     WTL=c(lin_WTL, exp_WTL))

knitr::kable(linexp, caption="GPP relation with environmental variable using linear and exponential equations (R2 values)")

```

These R2 values might be slightly different from those described in the "calibration" part concerning methane. That's because these values were obtained with linear regression (and transformation for the exponential model) whereas the others were obtained using non-linear algorithms.


